---
title: Bubble Charts in R | Examples | Plotly
name: Bubble Charts
permalink: r/bubble-charts/
description: How to make a bubble chart in R. A bubble chart is a scatter plot whose markers have variable color and size.
layout: base
thumbnail: thumbnail/bubble.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: chart_type
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source! [Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/). 
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode. 
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Simple Bubble Chart

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

plot_ly(data, x = ~Women, y = ~Men, text = ~School, type = 'scatter', mode = 'markers', 
        marker = list(size = ~gap, opacity = 0.5)) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE))
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/simple")
```

### Setting Markers Color

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

plot_ly(data, x = ~Women, y = ~Men, text = ~School, type = 'scatter', mode = 'markers', 
        marker = list(size = ~gap, opacity = 0.5, color = 'rgb(255, 65, 54)')) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE))
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/color1")
```

### Setting Multiple Colors

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

colors <- c('rgba(204,204,204,1)', 'rgba(222,45,38,0.8)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)',
            'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 
            'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 
            'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)', 'rgba(204,204,204,1)',
            'rgba(204,204,204,1)')
# Note: The colors will be assigned to each observations based on the order of the observations in the dataframe.


plot_ly(data, x = ~Women, y = ~Men, text = ~School, type = 'scatter', mode = 'markers',
        marker = list(size = ~gap, opacity = 0.5, color = colors)) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE))
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/color2")
```

### Mapping a Color Variable (Continuous)

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

plot_ly(data, x = ~Women, y = ~Men, text = ~School, type = 'scatter', mode = 'markers', color = ~gap, colors = 'Reds',
        marker = list(size = ~gap, opacity = 0.5)) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE))
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/color3")
```

### Mapping a Color Variable (Categorical)

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

data$State <- as.factor(c('Massachusetts', 'California', 'Massachusetts', 'Pennsylvania', 'New Jersey', 'Illinois', 'Washington DC', 
                          'Massachusetts', 'Connecticut', 'New York', 'North Carolina', 'New Hampshire', 'New York', 'Indiana', 
                          'New York', 'Michigan', 'Rhode Island', 'California', 'Georgia', 'California', 'California'))

plot_ly(data, x = ~Women, y = ~Men, text = ~School, type = 'scatter', mode = 'markers', size = ~gap, color = ~State, colors = 'Paired',
        marker = list(opacity = 0.5, sizemode = 'diameter')) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE),
         showlegend = FALSE)
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/color4")
```

### Scaling the Size of Bubble Charts

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

data$State <- as.factor(c('Massachusetts', 'California', 'Massachusetts', 'Pennsylvania', 'New Jersey', 'Illinois', 'Washington DC', 
                          'Massachusetts', 'Connecticut', 'New York', 'North Carolina', 'New Hampshire', 'New York', 'Indiana', 
                          'New York', 'Michigan', 'Rhode Island', 'California', 'Georgia', 'California', 'California'))

plot_ly(data, x = ~Women, y = ~Men, type = 'scatter', mode = 'markers', size = ~gap, color = ~State, colors = 'Paired',
        marker = list(opacity = 0.5, sizemode = 'diameter', 
                #Controlling for the size of the bubbles:
				sizeref = 1.5),
        text = ~paste('School:', School, '<br>Gender gap:', gap)) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE),
         showlegend = FALSE)
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/size")
```

### Hover Text with Bubble Charts

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

data$State <- as.factor(c('Massachusetts', 'California', 'Massachusetts', 'Pennsylvania', 'New Jersey', 'Illinois', 'Washington DC', 
                          'Massachusetts', 'Connecticut', 'New York', 'North Carolina', 'New Hampshire', 'New York', 'Indiana', 
                          'New York', 'Michigan', 'Rhode Island', 'California', 'Georgia', 'California', 'California'))

plot_ly(data, x = ~Women, y = ~Men, type = 'scatter', mode = 'markers', size = ~gap, color = ~State, colors = 'Paired',
        marker = list(opacity = 0.5, sizemode = 'diameter', 
        sizeref = 1.5),
        text = ~paste('School:', School, '<br>Gender gap:', gap)) %>%
  layout(title = 'Gender Gap in Earnings per University',
         xaxis = list(showgrid = FALSE),
         yaxis = list(showgrid = FALSE),
         showlegend = FALSE)
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/hovertext")
```

### Styled Buble Chart

```{r, results = 'hide'}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/gapminderDataFiveYear.csv")

data_2007 <- data[which(data$year == 2007),]
data_2007 <- data_2007[order(data_2007$continent, data_2007$country),]
slope <- 2.666051223553066e-05
data_2007$size <- sqrt(data_2007$pop*slope)
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951')

plot_ly(data_2007, x = ~gdpPercap, y = ~lifeExp, color = ~continent, colors = colors, type = 'scatter', mode = 'markers',
        marker = list(symbol = 'circle', size = ~size, sizemode = 'diameter', sizeref = 0.85, 
                      line = list(width = 2, color = '#FFFFFF')),
        text = ~paste('Country:', country, '<br>Life Expectancy:', lifeExp, '<br>GDP:', gdpPercap,
                      '<br>Pop.:', pop)) %>%
  layout(title = 'Life Expectancy v. Per Capita GDP, 2007',
         xaxis = list(title = 'GDP per capita (2000 dollars)',
                      gridcolor = 'rgb(255, 255, 255)',
                      range = c(2.003297660701705, 5.191505530708712),
                      type = 'log',
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwidth = 2),
         yaxis = list(title = 'Life Expectancy (years)',
                      gridcolor = 'rgb(255, 255, 255)',
                      range = c(36.12621671352166, 91.72921793264332),
                      zerolinewidth = 1,
                      ticklen = 5,
                      gridwith = 2),
         paper_bgcolor = 'rgb(243, 243, 243)',
         plot_bgcolor = 'rgb(243, 243, 243)')
```

```{r, echo=FALSE}
plotly_POST(filename="bubble/styled")
```

#Reference

See [https://plot.ly/r/reference/#scatter](https://plot.ly/r/reference/#scatter) for more information and chart attribute options!
