---
title: R Graphing Library | Plotly
permalink: r/
description: Plotly's R graphing library makes interactive, publication-quality graphs online. Examples of how to make line plots, scatter plots, area charts, bar charts, error bars, box plots, histograms, heatmaps, subplots, multiple-axes, and 3D (WebGL based) charts.
layout: langindex
language: r
---

<h1 class="centered">Plotly R Library</h1>
<div class="row centered btnrow">
  <a href="/r/getting-started/" class="button no_underline">Getting Started</a>
  <a href="/r/base/" class="button no_underline">User Guide</a>
  <a href="https://plot.ly/r/reference/" class="button no_underline">Figure Reference</a>
  <a href="https://plot.ly/r/shiny-tutorial/" class="button no_underline">Shiny</a>
</div>

<div>Plotly for R is an interactive, browser-based charting library built on the open source javascript graphing library,
<a href="https://plot.ly/javascript" target="_blank">plotly.js</a>. It works entirely locally, through the <a href="http://www.htmlwidgets.org/" target="_blank">HTML widgets</a> framework.
</div>

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

```{r, results = 'hide'}
library(plotly)
set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]
plot_ly(d, x = ~carat, y = ~price, color = ~carat,
        size = ~carat, text = ~paste("Clarity: ", clarity))
```

```{r, echo=FALSE}
plotly_POST(filename="r-intro/scatter")
```

Plotly graphs are interactive. Click-drag to zoom, shift-click to pan, double-click to autoscale.

#### Know and love `ggplot2`? Try `ggplotly`

```{r, results = 'hide'}
p <- ggplot(data = d, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

ggplotly(p)
```

```{r, echo=FALSE}
plotly_POST(filename="r-intro/ggplot")
```

{% assign languagelistimg = site.posts | where:"page_type":"example_index" | where:"language","r"  | where:"has_thumbnail",true | sort: "order"  %}
{% assign languagelist = site.posts | where:"page_type":"example_index" | where:"language","r" %}

{% include documentation_eg.html %}

