---
title: Getting Started with Shiny and Plotly | Examples | Plotly
name: Getting Started with Shiny and Plotly
permalink: r/shiny-tutorial/
redirect_from:
  - ggplot2/shiny-tutorial/
  - r/shiny/
  - ggplot2/shiny/
description: Getting Started with Shiny and Plotly
layout: base
thumbnail: thumbnail/shiny-r.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: get_request
output: 
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# Plotly Graphs in Shiny

Since plotly adheres to the [htmlwidgets](http://www.htmlwidgets.org/) framework, it's easy to embed plotly graphs in [shiny](http://shiny.rstudio.com/) apps. Not only does this make it easy for your plotly graphs to change dynamically according to input values, but (thanks to `event_data()`) it is also easy to access user events with plotly graphs! Here is a fairly basic example of accessing hover events server-side:

<iframe src="https://plotly.shinyapps.io/Movies" width="100%" height=700 scrolling="no" seamless="seamless" style="border: none"></iframe>

```{r}
library(shiny)
library(plotly)

ui <- fluidPage(
  plotlyOutput("plot"),
  verbatimTextOutput("event")
)

server <- function(input, output) {
  
  # renderPlotly() also understands ggplot2 objects!
  output$plot <- renderPlotly({
    plot_ly(mtcars, x = ~mpg, y = ~wt)
  })
  
  output$event <- renderPrint({
    d <- event_data("plotly_hover")
    if (is.null(d)) "Hover on a point!" else d
  })
}

shinyApp(ui, server)
```

Check out our [shiny gallery](https://plot.ly/r/shiny-gallery/) for more examples!