---
title: Subplots in R | Plotly
name: Subplots
permalink: r/subplots/
description: How to graph subplots and small multiples in R with Plotly.
layout: base
thumbnail: /images/subplots.png
language: r
page_type: example_index
has_thumbnail: true
display_as: multiple_axes
order: 2
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
# Subplots

### Basic Subplot

```{r, message=FALSE}
library(plotly)
subplot(
  plot_ly(economics, x = date, y = uempmed, filename="r-docs/basic-subplot"),
  plot_ly(economics, x = date, y = unemploy),
  margin = 0.05
) %>% layout(showlegend = FALSE)
```

### Subplot Rows

Specify the number of rows with `nrows`.

```{r, message=FALSE}
# Basic subplot
library(plotly)
subplot(
  plot_ly(economics, x = date, y = uempmed, filename="r-docs/basic-subplot"),
  plot_ly(economics, x = date, y = unemploy),
  margin = 0.05,
  nrows=2
) %>% layout(showlegend = FALSE)
```

### Creating Subplots with `group`

A more powerful way to make subplots is by using the `group` argument to split the data into different plotly "traces" in conjunction with `subplot()`.

```{r, message=FALSE}
plot_ly(iris, x = Petal.Length, y = Petal.Width,
        group = Species, mode = "markers", filename="r-docs/grouped")
```

Together, `group` and `subplot()` can be used to anchor traces onto different axes. In this example, each trace binds itself to one of the 3 x axes with one of these arguments: `xaxis = "x1"`, `xaxis = "x2"`, `xaxis = "x3"`.

```{r, message=FALSE}
iris$id <- as.integer(iris$Species)
p <- plot_ly(iris, x = Petal.Length, y = Petal.Width, group = Species,
             xaxis = paste0("x", id), mode = "markers", filename="r-docs/grouped-axes")
subplot(p)
```

### Customizing Axes

You can customize each of these axes. "`x1`", "`x2`", "`x3`", etc assigned in the "traces" is related to "`xaxis`", "`xaxis2`", "`xaxis2`", "`xaxis3`" etc inside the plot's `layout`. [View the entire list of configurable axis properties](https://plot.ly/r/reference/#xaxis). Note that it is "`xaxis`" not "`xaxis1`".

```{r, message=FALSE}
p <- plot_ly(iris, x = Petal.Length, y = Petal.Width, group = Species,
             xaxis = paste0("x", id), mode = "markers", filename="r-docs/customized-axes")

layout(
    subplot(p),
    xaxis = list(title = "x axis 1", showgrid=FALSE),
    xaxis2 = list(title = "x axis 2", showgrid=FALSE),
    xaxis3 = list(title = "x axis 3", showgrid=FALSE),

    yaxis = list(title = "y axis 1", showgrid=FALSE),
    yaxis2 = list(title = "y axis 2", showgrid=FALSE),
    yaxis3 = list(title = "y axis 3", showgrid=FALSE)
)
```

If you are familar with [plotly.js](https://plot.ly/javascript-graphing-library), you might notice that `subplot` is generating axis objects with the appropriate anchor and domain properties. If you are interested, [view how subplots are created in plotly.js](https://plot.ly/javascript-graphing-library/subplots) or [view the JSON representation of this graph](https://plot.ly/~RplotBot/1408.json).

Since `subplot()` does not assume x/y axes are on a common scale, it does not impose any restrictions on the range by default. However, you can change this by pre-specifying the range of the [axis objects](https://plot.ly/r/reference/#xaxis) via the `layout()` function.

```{r, message=FALSE}
p <- plot_ly(iris, x = Petal.Length, y = Petal.Width, group = Species,
             xaxis = paste0("x", id), mode = "markers", filename="r-docs/restricted-axes")

p <- layout(
  p,
  xaxis = list(range = range(Petal.Length) + c(-0.1, 0.1)),
  yaxis = list(range = range(Petal.Width) + c(-0.1, 0.1))
)

subplot(p)
```

Note that the `xaxis` and `yaxis` properties that are specified in `layout` are transferred to all of the `xaxis` and `yaxis` keys that are created in the `subplot` command. The example above could also be written as:

```{r, message=FALSE}
p <- plot_ly(iris, x = Petal.Length, y = Petal.Width, group = Species,
             xaxis = paste0("x", id), mode = "markers", filename="r-docs/restricted-axes-2")

p <- subplot(p)
layout(p,
  xaxis = list(range = range(iris$Petal.Length) + c(-0.1, 0.1)),
  yaxis = list(range = range(iris$Petal.Width) + c(-0.1, 0.1)),

  xaxis2 = list(range = range(iris$Petal.Length) + c(-0.1, 0.1)),
  yaxis2 = list(range = range(iris$Petal.Width) + c(-0.1, 0.1)),

  xaxis3 = list(range = range(iris$Petal.Length) + c(-0.1, 0.1)),
  yaxis3 = list(range = range(iris$Petal.Width) + c(-0.1, 0.1))
)
```

So, if you would like all of your axes to have the same properties, assign the properties in `layout` before splitting the traces into subplots.

### Subplot Maps

Axes objects in maps are different than in cartesian `x`, `y` plots. With maps, each trace has a `geo` ID that assigns that trace the subplot with the same id. Just add a `geo = paste0("geo", id)` key inside `plot_ly` to assign traces to different subplots created with `subplot`.

```{r, message=FALSE, height=900}
# US map small multiples
library(plotly)
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/1962_2006_walmart_store_openings.csv')

# common map properties
g <- list(scope = 'usa', showland = T, landcolor = toRGB("gray90"), showcountries = F, subunitcolor = toRGB("white"))

# year text labels
yrs <- unique(df$YEAR)
id <- seq_along(yrs)
df2 <- data.frame(
  YEAR = yrs,
  id = id
)

# id for anchoring traces on different plots
df$id <- as.integer(factor(df$YEAR))

p <- plot_ly(df, type = 'scattergeo', lon = LON, lat = LAT, group = YEAR,
             geo = paste0("geo", id),
             showlegend = F, marker = list(color = toRGB("blue"), opacity = 0.5),
             filename="r-docs/map-subplots") %>%
  add_trace(lon = -78, lat = 47, mode = 'text', group = YEAR,
            geo = paste0("geo", id),
            text = YEAR, data = df2) %>%
  layout(title = 'New Walmart Stores per year 1962-2006<br> Source: <a href="http://www.econ.umn.edu/~holmes/data/WalMart/index.html">University of Minnesota</a>',
         geo = g,
         autosize = F,
         width = 1000,
         height = 900,
         hovermode = F)

subplot(p, nrows = 9)
```

[View more examples of maps in plotly and R.](https://plot.ly/r/#maps)
