---
title: Box Plots in R | Examples | Plotly
name: Box Plots
permalink: r/box-plots/
description: How to make an interactive box plot in R. Examples of box plots in R that are grouped, colored, and display the underlying data distribution.
layout: base
thumbnail: thumbnail/box.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: statistical
order: 1
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Boxplot

```{r, results = "hide"}
library(plotly)
plot_ly(y = ~rnorm(50), type = "box") %>%
  add_trace(y = ~rnorm(50, 1))
```

```{r, echo=FALSE}
plotly_POST(filename="box/1")
```

### Adding Jittered Points

```{r, results = "hide"}
plot_ly(y = ~rnorm(50), type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8)
```

```{r, echo=FALSE}
plotly_POST(filename="box/2")
```


### Several Box Plots

```{r, results = "hide"}
plot_ly(ggplot2::diamonds, y = ~price, color = ~cut, type = "box")
```

```{r, echo=FALSE}
plotly_POST(filename="box/3")
```

### Grouped Box Plots

```{r, results = "hide"}
plot_ly(ggplot2::diamonds, x = ~cut, y = ~price, color = ~clarity, type = "box") %>%
  layout(boxmode = "group")
```

```{r, echo=FALSE}
plotly_POST(filename="box/4")
```
