---
title: Bar Charts in R | Examples | Plotly
name: Bar Charts
permalink: r/bar-charts/
description: How to make a bar chart in R. Examples of grouped, stacked, overlaid, and colored bar charts.
layout: base
thumbnail: thumbnail/bar.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: chart_type
order: 4
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source! [Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/). 
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode. 
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Basic Bar Chart

```{r, results = 'hide'}
library(plotly)

plot_ly(
  x = c("giraffes", "orangutans", "monkeys"),
  y = c(20, 14, 23),
  name = "SF Zoo",
  type = "bar"
)
```

```{r, echo=FALSE}
plotly_POST(filename="bar/basic")
```

### Grouped Bar Chart

```{r, results = 'hide'}
library(plotly)

Animals <- c("giraffes", "orangutans", "monkeys")
SF_Zoo <- c(20, 14, 23)
LA_Zoo <- c(12, 18, 29)
data <- data.frame(Animals, SF_Zoo, LA_Zoo)

plot_ly(data, x = ~Animals, y = ~SF_Zoo, type = 'bar', name = 'SF Zoo') %>%
  add_trace(y = ~LA_Zoo, name = 'LA Zoo') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'group')
```

```{r, echo=FALSE}
plotly_POST(filename="bar/grouped")
```

### Stacked Bar Chart

```{r, results = 'hide'}
library(plotly)

Animals <- c("giraffes", "orangutans", "monkeys")
SF_Zoo <- c(20, 14, 23)
LA_Zoo <- c(12, 18, 29)
data <- data.frame(Animals, SF_Zoo, LA_Zoo)

plot_ly(data, x = ~Animals, y = ~SF_Zoo, type = 'bar', name = 'SF Zoo') %>%
  add_trace(y = ~LA_Zoo, name = 'LA Zoo') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack')
```

```{r, echo=FALSE}
plotly_POST(filename="bar/stacked")
```

### Bar Chart with Hover Text

```{r, results = 'hide'}
library(plotly)

x <- c('Product A', 'Product B', 'Product C')
y <- c(20, 14, 23)
text <- c('27% market share', '24% market share', '19% market share')
data <- data.frame(x, y, text)

plot_ly(data, x = ~x, y = ~y, type = 'bar', text = text,
        marker = list(color = 'rgb(158,202,225)',
                      line = list(color = 'rgb(8,48,107)', 
                      			  width = 1.5))) %>%
  layout(title = "January 2013 Sales Report",
         xaxis = list(title = ""),
         yaxis = list(title = ""))
```

```{r, echo=FALSE}
plotly_POST(filename="bar/text")
```

### Styled Bar Chart with Direct Labels

```{r, results = 'hide'}
library(plotly)

x <- c('Product A', 'Product B', 'Product C')
y <- c(20, 14, 23)
text <- c('27% market share', '24% market share', '19% market share')
data <- data.frame(x, y, text)

plot_ly(data, x = ~x, y = ~y, type = 'bar', text = text,
        marker = list(color = 'rgb(158,202,225)',
                      line = list(color = 'rgb(8,48,107)', width = 1.5))) %>%
  layout(title = "January 2013 Sales Report",
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         annotations = list(x = x, y = y, text = y,
                            xanchor = 'center', yanchor = 'bottom', 
                            showarrow = FALSE))
```

```{r, echo=FALSE}
plotly_POST(filename="bar/labels")
```

### Rotated Bar Chart Labels

```{r, results = 'hide'}
library(plotly)

x <- c('January', 'February', 'March', 'April', 'May', 'June', 'July', 'August', 'September', 'October', 'November', 'December')
y1 <- c(20, 14, 25, 16, 18, 22, 19, 15, 12, 16, 14, 17)
y2 <- c(19, 14, 22, 14, 16, 19, 15, 14, 10, 12, 12, 16)
data <- data.frame(x, y1, y2)

#The default order will be alphabetized unless specified as below:
data$x <- factor(data$x, levels = data[["x"]])

plot_ly(data, x = ~x, y = ~y1, type = 'bar', name = 'Primary Product', marker = list(color = 'rgb(49,130,189)')) %>%
  add_trace(y = ~y2, name = 'Secondary Product', marker = list(color = 'rgb(204,204,204)')) %>%
  layout(xaxis = list(title = "", tickangle = -45),
         yaxis = list(title = ""),
         margin = list(b = 100),
         barmode = 'group')
```

```{r, echo=FALSE}
plotly_POST(filename="bar/rotated")
```

### Customizing Bar Color

```{r, results = 'hide'}
library(plotly)

x <- c('Feature A', 'Feature B', 'Feature C', 'Feature D', 'Feature E')
y <- c(20, 14, 23, 25, 22)
data <- data.frame(x, y)

plot_ly(data, x = ~x, y = ~y, type = 'bar', color = I("black")) %>%
  layout(title = "Features",
         xaxis = list(title = ""),
         yaxis = list(title = ""))
```

```{r, echo=FALSE}
plotly_POST(filename="bar/color")
```

### Customizing Individual Bar Colors

```{r, results = 'hide'}
library(plotly)

x <- c('Feature A', 'Feature B', 'Feature C', 'Feature D', 'Feature E')
y <- c(20, 14, 23, 25, 22)
data <- data.frame(x, y)

plot_ly(data, x = ~x, y = ~y, type = 'bar',
        marker = list(color = c('rgba(204,204,204,1)', 'rgba(222,45,38,0.8)',
                                'rgba(204,204,204,1)', 'rgba(204,204,204,1)',
                                'rgba(204,204,204,1)'))) %>%
  layout(title = "Least Used Features",
         xaxis = list(title = ""),
         yaxis = list(title = ""))
```

```{r, echo=FALSE}
plotly_POST(filename="bar/colors")
```

### Mapping a Color Variable

```{r, results = 'hide'}
library(plotly)
library(dplyr)

ggplot2::diamonds %>% count(cut, clarity) %>%
  plot_ly(x = ~cut, y = ~n, color = ~clarity)
```

```{r, echo=FALSE}
plotly_POST(filename="bar/colorvar")
```

### Colored and Styled Bar Chart

```{r, results = 'hide'}
library(plotly)

x <- c(1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012)
roW <- c(219, 146, 112, 127, 124, 180, 236, 207, 236, 263, 350, 430, 474, 526, 488, 537, 500, 439)
China <- c(16, 13, 10, 11, 28, 37, 43, 55, 56, 88, 105, 156, 270, 299, 340, 403, 549, 499)
data <- data.frame(x, roW, China)

plot_ly(data, x = ~x, y = ~roW, type = 'bar', name = 'Rest of the World', 
        marker = list(color = 'rgb(55, 83, 109)')) %>%
  add_trace(y = ~China, name = 'China', marker = list(color = 'rgb(26, 118, 255)')) %>%
  layout(title = 'US Export of Plastic Scrap',
         xaxis = list(
           title = "",
           tickfont = list(
             size = 14, 
             color = 'rgb(107, 107, 107)')),
         yaxis = list(
           title = 'USD (millions)',
           titlefont = list(
             size = 16, 
             color = 'rgb(107, 107, 107)'),
           tickfont = list(
             size = 14,
             color = 'rgb(107, 107, 107)')),
         legend = list(x = 0, y = 1, bgcolor = 'rgba(255, 255, 255, 0)', bordercolor = 'rgba(255, 255, 255, 0)'),
         barmode = 'group', bargap = 0.15, bargroupgap = 0.1)
```

```{r, echo=FALSE}
plotly_POST(filename="bar/style")
```

### Waterfall Bar Chart

```{r, results = 'hide'}
library(plotly)

x <- c('Product<br>Revenue', 'Services<br>Revenue', 'Total<br>Revenue', 'Fixed<br>Costs', 'Variable<br>Costs', 'Total<br>Costs', 'Total')
y <- c(400, 660, 660, 590, 400, 400, 340) 
base <- c(0, 430, 0, 570, 370, 370, 0)
revenue <- c(430, 260, 690, 0, 0, 0, 0)
costs <- c(0, 0, 0, 120, 200, 320, 0)
profit <- c(0, 0, 0, 0, 0, 0, 370)
text <- c('$430K', '$260K', '$690K', '$-120K', '$-200K', '$-320K', '$370K')
data <- data.frame(x, base, revenue, costs, profit, text)

#The default order will be alphabetized unless specified as below:
data$x <- factor(data$x, levels = data[["x"]])

plot_ly(data, x = ~x, y = ~base, type = 'bar', marker = list(color = 'rgba(1,1,1, 0.0)')) %>%
  add_trace(y = ~revenue, marker = list(color = 'rgba(55, 128, 191, 0.7)',
                                        line = list(color = 'rgba(55, 128, 191, 0.7)',
                                                    width = 2))) %>%
  add_trace(y = ~costs, marker = list(color = 'rgba(219, 64, 82, 0.7)',
                                      line = list(color = 'rgba(219, 64, 82, 1.0)',
                                                  width = 2))) %>%
  add_trace(y = ~profit, marker = list(color = 'rgba(50, 171, 96, 0.7)',
                                      line = list(color = 'rgba(50, 171, 96, 1.0)',
                                                  width = 2))) %>%
  layout(title = 'Annual Profit - 2015',
         xaxis = list(title = ""),
         yaxis = list(title = ""),
         barmode = 'stack',
         paper_bgcolor = 'rgba(245, 246, 249, 1)',
         plot_bgcolor = 'rgba(245, 246, 249, 1)',
         showlegend = FALSE) %>%
  add_annotations(text = text, 
                  x = x,
                  y = y,
                  xref = "x",
                  yref = "y",
                  font = list(family = 'Arial', 
                              size = 14, 
                              color = 'rgba(245, 246, 249, 1)'),
                  showarrow = FALSE)
```

```{r, echo=FALSE}
plotly_POST(filename="bar/waterfall")
```

### Bar Chart with Relative Barmode

```{r, results = 'hide'}
library(plotly)

x <- c(1, 2, 3, 4)
y1 <- c(1, 4, 9, 16)
y2 <- c(6, -8, -4.5, 8)
y3 <- c(-15, -3, 4.5, -8)
y4 <- c(-1, 3, -3, -4)

data <- data.frame(x, y1, y2, y3, y4)

plot_ly(data, x = ~x, y = ~y1, type = 'bar', name = 'Trace 1') %>%
  add_trace(y = ~y2, name = 'Trace 2') %>%
  add_trace(y = ~y3, name = 'Trace 3') %>%
  add_trace(y = ~y4, name = 'Trace 4') %>%
  layout(title = 'Relative Barmode',
         xaxis = list(title = 'X axis'),
         yaxis = list(title = 'Y axis'),
         barmode = 'relative')
```

```{r, echo=FALSE}
plotly_POST(filename="bar/relative")
```

### Horizontale Bar Chart

See examples of horizontal bar charts [here](https://plot.ly/r/horizontal-bar-charts/).

#Reference

See [https://plot.ly/r/reference/#bar](https://plot.ly/r/reference/#bar) for more information and chart attribute options!

