---
title: Legends in R | Examples | Plotly
name: Legends
permalink: r/legend/
description: How to modify the legend in R graphs. Seven examples of how to move, color, and hide the legend.
layout: base
thumbnail: thumbnail/legends.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Legend Names
```{r, results = 'hide'}
library(plotly)
p <- plot_ly(x = ~seq(1, 8)) %>%
  add_lines(y = ~rnorm(8), name = "Blue Trace") %>%
  add_lines(y = ~rnorm(8), name = "Orange Trace")
p
```

```{r, echo=FALSE}
plotly_POST(filename="legend/names")
```

### Hiding the Legend

```{r, results = 'hide'}
p %>% layout(showlegend = FALSE)
```

```{r, echo=FALSE}
plotly_POST(filename="legend/hiding")
```

### Positioning the Legend

```{r, results = 'hide'}
p %>% layout(legend = list(x = 0.5, y = 0))
```

```{r, echo=FALSE}
plotly_POST(filename="legend/position")
```

### Styling the Legend

```{r, results = 'hide'}
f <- list(
  family = "sans-serif",
  size = 12,
  color = "#000"
)
l <- list(
  font = f,
  bgcolor = "#E2E2E2",
  bordercolor = "#FFFFFF",
  borderwidth = 2
)
p %>% layout(legend = l)
```

```{r, echo=FALSE}
plotly_POST(filename="legend/style")
```

### Hiding Legend Entries

```{r, results = 'hide'}
plot_ly(x = ~seq(1, 8)) %>%
  add_trace(y = ~rnorm(8), showlegend = FALSE) %>%
  add_trace(y = ~rnorm(8), name = "Orange Trace")
```

```{r, echo=FALSE}
plotly_POST(filename="legend/entry")
```
