---
title: Line and Scatter Plots in R | Examples | Plotly
name: Line and Scatter Plots
permalink: r/line-and-scatter/
description: How to create line and scatter plots in R. Examples of basic and advanced scatter plots, time series line plots, colored charts, and density plots.
layout: base
thumbnail: thumbnail/line-and-scatter.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: chart_type
order: 1
output: 
  html_document:
    keep_md: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, results = 'hide')
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

# Line and Scatter Plots in R

### Simple scatterplot

```{r}
library(plotly)
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length)
p
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/basic")
```

### Scatter Plot with Qualitative Colorscale

```{r}
add_markers(p, color = ~Species)
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/color")
```

### ColorBrewer Palette Names

```{r}
add_markers(p, color = ~Species, colors = "Set1")
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/colorbrewer")
```

### Custom Color Scales

The `colors` argument also accepts a character vector of any valid R color code(s).

```{r}
pal <- c("red", "blue", "green")
add_markers(p, color = ~Species, colors = pal)
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/color-custom")
```

To ensure a particular data value gets mapped to particular color, provide a character vector of color codes, and match the names attribute accordingly.

```{r}
pal <- setNames(pal, c("virginica", "setosa", "versicolor"))
add_markers(p, color = ~Species, colors = pal)
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/color-custom2")
```

### Plotting markers and lines, efficiently

```{r}
add_trace(p, color = ~Species, mode = "markers+lines")
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/pointsAndLines")
```

## Mapping data to symbol and linetype

```{r}
add_trace(p, symbol = ~Species, linetype = ~Species)
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/symbolAndLinetype")
```

### Adding Color and Size Mapping

```{r}
d <- diamonds[sample(nrow(diamonds), 1000), ]
plot_ly(
  d, x = ~carat, y = ~price,
  text = ~paste("Clarity: ", clarity),
  color = ~carat, size = ~carat
)
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/colorAndSize")
```

### Density Plot

```{r}
dens <- with(diamonds, tapply(price, INDEX = cut, density))
df <- data.frame(
  x = unlist(lapply(dens, "[[", "x")),
  y = unlist(lapply(dens, "[[", "y")),
  cut = rep(names(dens), each = length(dens[[1]]$x))
)
plot_ly(df, x = ~x, y = ~y, color = ~cut) %>%
  add_lines()
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/colorDensity")
```

### Line Interpolation Options

```{r}
x <- 1:5
y <- c(1, 3, 2, 3, 1)
plot_ly(x = ~x) %>%
  add_lines(y = ~y, name = "linear", line = list(shape = "linear")) %>%
  add_lines(y = y + 5, name = "spline", line = list(shape = "spline")) %>%
  add_lines(y = y + 10, name = "vhv", line = list(shape = "vhv")) %>%
  add_lines(y = y + 15, name = "hvh", line = list(shape = "hvh")) %>%
  add_lines(y = y + 20, name = "vh", line = list(shape = "vh")) %>%
  add_lines(y = y + 25, name = "hv", line = list(shape = "hv"))
```

```{r, echo=FALSE}
plotly_POST(filename="scatter/interp")
```
