---
title: Download Plotly Graphs into R
name: Get Requests
permalink: r/get-requests/
description: How to download plotly users's public graphs and data with R.
layout: base
thumbnail: thumbnail/get-requests.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: get_request
---

# Downloading Plotly Graphs into R

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, results = 'hide')
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

Download Plotly figures directly into R with `get_figure()`. This takes the `username` and the `plot_id` as arguments.

For example, to download [https://plot.ly/~cpsievert/559](https://plot.ly/~cpsievert/559) into R, call:

```{r}
library(plotly)
fig <- get_figure("cpsievert", "559")
```

<br>
Once the figure is downloaded, you can edit it like any plotly object. This will create a new figure unless you specify the same filename as the figure that you downloaded.

```{r}
layout(fig, title = paste("Modified on ", Sys.time()))
```

```{r, echo=FALSE}
plotly_POST(filename="getRequests/modify")
```

### Adding a trace to a subplot figure

```{r}
fig <- get_figure("chelsea_lyn", "6343")
add_lines(fig, x = c(1, 2), y = c(1, 2), xaxis = "x2", yaxis = "y2")
```

```{r, echo=FALSE}
plotly_POST(filename="getRequests/subplot")
```

### Restyle traces

It's easy to add a trace or change the layout of figure, but it's a bit more challenging to modify attributes of an existing trace. If you know the attribute you want to change, and the trace number (starting with 1), use the `style()` function. For example, we could remove the hover text from [this plot](https://plot.ly/~RPlotBot/2833) like so:

```{r}
fig <- get_figure("rplotbot", 2833)
fig %>% 
  style(hoverinfo = "none") %>% 
  layout(title = "No hover text")
```

```{r, echo=FALSE}
plotly_POST(filename="getRequests/style")
```

You'll probably want to inspect the traces before you use this function, and I recommend using the `plotly_json()` function to do so.
