---
title: Using Plotly with knitr
name: Using Plotly with knitr
permalink: r/knitr/
description: How to embed Plotly graphs in knitr documents.
layout: base
language: r
page_type: example_index
has_thumbnail: true
display_as: file_settings
order: 5
---

## Embedding plotly graphs in knitr documents


```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

Simply printing `plotly` objects in the R console will create a new plotly figure in your online plotly account and open your web-browser to view it.

```{r, message=FALSE, height=800}
library(plotly)
p <- plot_ly(economics, x = date, y = uempmed, filename="r-docs/knitr-example")
```

If you are using knitr/R Markdown with HTML output, printing the `plotly` object will not only create the plot but embed it in the HTML as an iframe. This document itself is written with R Markdown, so printing `p` embeds the figure.


```{r, message=FALSE}
p
```

You can set the width and the height of the plot with `width` and `height` code chunk parameters. For example:

`{r, height=800}`

```{r, height=800}
p
```

If you are using [Plotly Offline with R Studio](https://purchasing.plot.ly/plotly-offline-r), then printing the plotly object in knitr will also include the necessary `plotly.js` files to draw the graph: the graph is rendered locally inside the document.
