---
title: Using Plotly with rmarkdown/knitr
name: Using Plotly with rmarkdown/knitr 
permalink: r/knitr/
redirect_from:
  - r/embedding-plotly-graphs-in-HTML
description: How to embed Plotly graphs in Rmd files.
layout: base
language: r
page_type: example_index
has_thumbnail: true
display_as: file_settings
order: 5
output:
  html_document:
    highlight: null
    keep_md: yes
    theme: null
---

## Embedding plotly graphs in Rmd files

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

If you are using [rmarkdown](http://rmarkdown.rstudio.com/) with HTML output, printing a `plotly` object in a code chunk will result in an interactive HTML graph. When using rmarkdown with non-HTML output, printing a `plotly` object will result in a png screenshot of the graph.

```{r, results = "hide"}
library(plotly)
p <- plot_ly(economics, x = ~date, y = ~unemploy / pop)
p
```

```{r, echo=FALSE}
plotly_POST(filename='r-docs/knitr-example')
```

Sometimes, you may want to print a _list_ of plotly objects. If, for some reason, you don't want to use the [`subplot()` function](https://plot.ly/r/subplots/), you can print a list of htmlwidgets in a single code chunk using the `tagList()` function from the **htmltools** package:

```{r, results = "hide"}
htmltools::tagList(list(p, p))
```

You can also host your figures on a plotly server via `plotly_POST()` which returns a figure object. When a figure object is printed in an rmarkdown/knitr document, it embeds the figure as an iframe, displaying the plot as it appears on your plotly account.

```{r, results='hide'}
f <- plotly_POST(p)
class(f)
f
```

You can control the height/width of that iframe through the `height`/`width` [knitr chunk options](http://yihui.name/knitr/options/), but the figure object also contains the relevant url so you complete control over embedding your figure. The post has more details on how to [embed plotly graphs with HTML iframes](http://help.plot.ly/embed-graphs-in-websites/), but could also use plotly's built-in image export by simply adding a `.png` (or similar) extension.

```{r}
htmltools::tags$img(src = paste0(f[["url"]], ".png"))
```

