---
title: Getting Started with Shiny and Plotly | Examples | Plotly
name: Getting Started with Shiny and Plotly
permalink: r/shiny-tutorial/
redirect_from:
  - ggplot2/shiny-tutorial/
  - r/shiny/
  - ggplot2/shiny/
description: Getting Started with Shiny and Plotly
layout: base
thumbnail: /images/shiny-r.png
language: r
page_type: example_index
has_thumbnail: false
display_as: get_request
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

# Plotly Graphs in Shiny

Plotly works with Shiny entirely *client-side* either through [plotly.js](https://plot.ly/javascript) or with Plotly's [postMessage API](https://github.com/plotly/postMessage-API). This means that updating the Plotly graphs is *fast* because no external calls are made to a Plotly server. You can export Plotly graphs to your account by clicking the <code>Edit chart</code> link on the bottom right of the chart.



<iframe src="https://plotly.shinyapps.io/Movies" width="100%" height=700 scrolling="no" seamless="seamless" style="border: none"></iframe>



### Example 1 - Plotly's Native Syntax

#### `ui.R`
```{r, message=FALSE}

library(shiny)
library(plotly)

shinyUI(fluidPage(
  titlePanel("Movie Ratings!"),
  sidebarPanel(
    sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 10)
  ),
  mainPanel(
    plotlyOutput("trendPlot")
  )
))
```

#### `server.R`
```{r, message=FALSE}
library(shiny)
library(plotly)

data(movies, package = "ggplot2")
minx <- min(movies$rating)
maxx <- max(movies$rating)

shinyServer(function(input, output) {

  output$trendPlot <- renderPlotly({
    # size of the bins depend on the input 'bins'
    size <- (maxx - minx) / input$bins

    # a simple histogram of movie ratings
    p <- plot_ly(movies, x = rating, autobinx = F, type = "histogram",
                 xbins = list(start = minx, end = maxx, size = size))
    # style the xaxis
    layout(p, xaxis = list(title = "Ratings", range = c(minx, maxx), autorange = F,
                           autotick = F, tick0 = minx, dtick = size))
  })
})
```

### Example 2 - Render `ggplotly`

#### `ui.R`
```{r, message=FALSE}
library(shiny)
library(plotly)

shinyUI(fluidPage(
  titlePanel("Movie Ratings!"),
  sidebarPanel(
    sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 10)
  ),
  mainPanel(
    plotlyOutput("trendPlot")
  )
))
```

#### `server.R`
```{r, message=FALSE}
library(shiny)
library(plotly)

data(movies, package = "ggplot2")
minx <- min(movies$rating)
maxx <- max(movies$rating)

shinyServer(function(input, output) {

  output$trendPlot <- renderPlotly({
    # size of the bins depend on the input 'bins'
    size <- (maxx - minx) / input$bins

    gg <- ggplot(movies, aes(x=rating)) +
                 geom_histogram(aes(y = ..density..), binwidth=size)
    # Convert the ggplot to a plotly
    p <- ggplotly(gg)
    p
  })
})
```
