---
title: Embed Graphs in HTML
name: Embed Graphs in HTML
permalink: r/embedding-plotly-graphs-in-HTML
description: How to embed Plotly graphs in HTML pages with Plotly's R API
layout: base
thumbnail: text-and-annotations.png
language: r
page_type: example_index
has_thumbnail: false
display_as: layout_opt
---

# Embed Graphs in HTML

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

As of version 2.0, plotly's R package utilizes the [htmlwidgets](http://www.htmlwidgets.org/) framework. As a result, printing objects of class "plotly" in [rmarkdown/knitr HTML documents](http://rmarkdown.rstudio.com/html_document_format.html) will embed the necessary HTML/JavaScript to create the client-side visualization (via [plotly.js](http://plot.ly/javascript)).

```{r}
library(plotly)
p <- plot_ly(midwest, x = percollege, color = state, type = "box")
class(p)
p
```

You can also post your figure to a plotly server with `plotly_POST()`. This function returns an object of class figure. When you print a figure object in an rmarkdown/knitr document, it embeds the figure as an iframe (pointing to your figure).

```{r}
f <- plotly_POST(p, filename = "r-docs/midwest-boxplots")
class(f)
f
```

If you want more control over embedding graphs hosted on <https://plot.ly>, [learn how to embed plotly graphs with HTML iframes](http://help.plot.ly/embed-graphs-in-websites/)
