---
title: Using Plotly with knitr
name: Using Plotly with knitr
permalink: r/knitr/
description: How to embed Plotly graphs in knitr documents.
layout: base
language: r
page_type: example_index
has_thumbnail: true
display_as: file_settings
order: 5
---

## Embedding plotly graphs in knitr documents

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

Simply printing `plotly` objects in the R console will render your chart in the web browser or in RStudio's viewer.

If you are using knitr/R Markdown with HTML output, printing the `plotly` object will embed the graph in the HTML.


```{r, results='hide'}
library(plotly)
p <- plot_ly(economics, x = date, y = unemploy / pop)
p
```

```{r, echo=FALSE, message=FALSE}
plotly_POST(p, filename='r-docs/knitr-example')
```

If your hosting your graphs in your online plotly account through `plotly_POST`, printing the figure will embed the graph as an iframe.

```{r}
plotly_POST(p, filename='r-docs/knitr-example')
```

## Embedding Multiple Plots in a knitR chunk

```{r}
library(plotly)

p <- plot_ly(economics, x = date, y = uempmed, name = "unemployment")
p <- p %>% add_trace(y = fitted(loess(uempmed ~ as.numeric(date))), x = date)

p2 <- plot_ly(data = iris, x = Sepal.Length, y = Petal.Length, mode = "markers", color = Species)

htmltools::tagList(list(as.widget(p), as.widget(p2)))
```
