---
title: R Filenames, Folders, and Updating Plotly Graphs in R | Examples | Plotly
name: Filenames, Folders, and Updating Plotly Graphs in R
permalink: r/file-options/
description: How to update your graphs in R with the fileopt parameter.
layout: base
language: r
page_type: example_index
has_thumbnail: false
display_as: file_settings
---

# Setting Filenames and Overwriting Plotly Graphs in R

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

To create a plotly figure on a plotly server, use `plotly_POST()`.

```{r}
library(plotly)
p <- plot_ly(x = c(1, 2), y = c(1, 2))
plotly_POST(p)
```

<br>

If you don't include a filename, a new plot will be made on your online plotly account. If you want to overwrite a plot (i.e., keep the graph served from the same plotly URL), specify a filename. This implicitly overwrites your plotly graph.

```{r}
plotly_POST(p, filename = "name-of-my-plotly-file")
```

If the filename contains "/", it will automatically create a plotly folder.

```{r}
plotly_POST(p, filename="r-docs/name-of-my-plotly-file")
```

View your Plotly graphs at [https://plot.ly/organize](https://plot.ly/organize).
