---
title: 3D Tri-Surf Plots in R | Examples | Plotly
name: 3D Tri-Surf Plots
permalink: r/trisurf/
description: How to make interactive 3D mesh plots in R.
layout: base
thumbnail: thumbnail/trisurf.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: 3d_charts
order: 17
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```
### Basic Tri-Surf Plot

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
  x = c(0, 1, 2, 0),
  y = c(0, 0, 1, 2),
  z = c(0, 2, 0, 1),
  i = c(0, 0, 0, 1),
  j = c(1, 2, 3, 2),
  k = c(2, 3, 1, 3),
  facecolor = toRGB(viridisLite::viridis(4))
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="trisurf/1")
chart_link
```

```{r, echo=FALSE}
chart_link
```


### Cube with Different Face Colors

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
  x = c(0, 0, 1, 1, 0, 0, 1, 1),
  y = c(0, 1, 1, 0, 0, 1, 1, 0),
  z = c(0, 0, 0, 0, 1, 1, 1, 1),
  i = c(7, 0, 0, 0, 4, 4, 2, 6, 4, 0, 3, 7),
  j = c(3, 4, 1, 2, 5, 6, 5, 5, 0, 1, 2, 2),
  k = c(0, 7, 2, 3, 6, 7, 1, 2, 5, 5, 7, 6),
  facecolor = rep(toRGB(viridisLite::inferno(6)), each = 2)
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="trisurf/2")
chart_link
```

```{r, echo=FALSE}
chart_link
```

