---
title: Buttons in R | Examples | Plotly
name: Buttons
permalink: r/custom-buttons/
description: How to create mixed subplots in R with Plotly.
layout: base
thumbnail: thumbnail/mixed_subplots.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: controls
order:
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Styles

```{r, results = 'hide'}
library(plotly)

x <- seq(-2*pi, 2*pi, length.out = 1000)
df <- data.frame(x, y1 = sin(x), y2 = cos(x))

p <- plot_ly(df, x = ~x) %>%
  add_lines(y = ~y1, name = "A") %>%
  add_lines(y = ~y2, name = "B", visible = F)


p <- p %>% layout(
  title = "Drop down menus - Styling",
  xaxis = list(domain = c(0.1, 1)),
  yaxis = list(title = "y"),
  updatemenus = list(
    list(
      type = "buttons",
      y = 0.8,
      buttons = list(
        
        list(method = "restyle",
             args = list("line.color", "blue"),
             label = "Blue"),
        
        list(method = "restyle",
             args = list("line.color", "red"),
             label = "Red")))
  ))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="buttons/basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Chart Types

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(z = ~volcano, type = "heatmap", colorscale='Viridis')

p <- p %>% layout(
  title = "Buttons",
  xaxis = list(domain = c(0.1, 1)),
  yaxis = list(title = "y"),
  updatemenus = list(
    list(
      type = "buttons",
      direction = "right",
      yanchor = "top",
      x = 0.8,
      y = 1,
      buttons = list(
        
        list(method = "restyle",
             args = list("type", "heatmap"),
             label = "heatmap"),
        
        list(method = "restyle",
             args = list("type", "contour"),
             label = "contour"),
        
        list(method = "restyle",
             args = list("type", "surface"),
             label = "surface"),
        
        list(method = "restyle",
             args = list("reversescale", TRUE),
             label = "Reverse"),
        
        list(method = "restyle",
            args = list("colorscale", "Rainbow"),
            label = "Rainbow"),
        
        list(method = "restyle",
             args = list("colorscale", "Jet"),
             label = "Jet"),
        
        list(method = "restyle",
             args = list("colorscale", "Earth"),
             label = "Earth"),
        
        list(method = "restyle",
             args = list("colorscale", "Electric"),
             label = "Electric")
        ))
  ))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="buttons/3d")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Wind Energy Farms

```{r, results = 'hide'}
library(plotly)

#Sys.setenv('MAPBOX_TOKEN', 'your token here') 

# read in wind turbines and farms data
df_wind = read.csv('https://plot.ly/~datasets/2805.csv')
df_farms = read.csv('https://plot.ly/~jackp/17256.csv')

# subset and clean data
df_sub <- subset(df_wind, manufac != "unknown", select=c(lat_DD, long_DD, manufac))
df_farms$Longitude = as.numeric(gsub("'", "", df_farms$Longitude))
df_farms$Wind.Farm = gsub("^((\\w+\\W+){2}).*","\\1",df_farms$Wind.Farm)
rm(df_wind)


# location buttons for the plot
usa <- list(method = "relayout",
            args = list(list(mapbox.center.lat = median(df_sub$lat_DD),
                        mapbox.center.lon = median(df_sub$long_DD),
                        mapbox.zoom = 3)),
            label = "USA")

buttons <- function(i) {
  list(method = "relayout",
       args = list(list(mapbox.center.lat = df_farms$Latitude[i],
                   mapbox.center.lon = df_farms$Longitude[i],
                   mapbox.zoom = 9)),
       label = df_farms$Wind.Farm[i]) 
}

# map style buttons for the plot
basic <- list(method = "relayout",
             args = list(list(mapbox.style = "basic")),
             label = "Basic")

dark <- list(method = "relayout",
            args = list(list(mapbox.style = "dark")),
            label = "Dark")

satellite <- list(method = "relayout",
             args = list(list(mapbox.style = "satellite")),
             label = "Satellite")  

# plot scattermapbox with buttons 
p <- plot_mapbox(df_sub, lat = ~lat_DD, lon = ~long_DD, mode = 'scattermapbox',
                 split = ~manufac, size=3) %>%
  add_annotations(x = 0.05, y = 0.05,
                  text = "All US wind turbines (scroll to zoom)",
                  xref = "page",
                  yref = "page",
                  showarrow = FALSE,
                  font = list(color = 'magenta',
                              size = 14)) %>%
  layout(plot_bgcolor = 'black', 
         paper_bgcolor = 'black', 
         mapbox = list(center = list(lat = median(df_sub$lat_DD), 
                                     lon = median(df_sub$long_DD)), 
                       zoom = 3, style = 'dark'),
         updatemenus = list(list(type='buttons',
                                 direction = "right",
                                 xanchor = 'center',
                                 yanchor = "top",
                                 pad = list('r'= 0, 't'= 10, 'b' = 10),
                                 x = 0.5,
                                 y = 1,
                                 showactive = FALSE,
                                 buttons=list(usa, buttons(1),
                                              buttons(2), buttons(3), 
                                              buttons(4), buttons(5))),
                            list(type='buttons',
                                 direction = "right",
                                 xanchor = 'center',
                                 yanchor = "top",
                                 pad = list('r'= 0, 't'= 10),
                                 x = 0.5,
                                 y = 0.95,
                                 showactive = FALSE,
                                 buttons=list(buttons(6), buttons(7),
                                              buttons(8), buttons(9),
                                              buttons(10), buttons(11))),
                            list(type='buttons',
                                 direction = "right",
                                 yanchor = "bottom",
                                 x = 1,
                                 y = 0,
                                 buttons=list(dark,basic,satellite)))) 


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="buttons/wind-turbine")
chart_link
```

```{r, echo=FALSE}
chart_link
```

#Reference

See [https://plot.ly/r/reference/#layout-updatemenus](https://plot.ly/r/reference/#layout-updatemenus) for more information and options!