---
title: Lines on Maps in R | Examples | Plotly
name: Lines on Maps
permalink: r/lines-on-maps/
description: How to draw lines, great circles, and contours on maps in R. Lines on maps can show distance between geographic points or be contour lines (isolines, isopleths, or isarithms).
layout: base
thumbnail: thumbnail/flight-paths.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: maps
order: 3
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Flight Paths Map

```{r, results = 'hide'}
library(plotly)
library(dplyr)
# airport locations
air <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_us_airport_traffic.csv')
# flights between airports
flights <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv')
flights$id <- seq_len(nrow(flights))

# map projection
geo <- list(
  scope = 'north america',
  projection = list(type = 'azimuthal equal area'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  countrycolor = toRGB("gray80")
)

p <- plot_geo(locationmode = 'USA-states', color = I("red")) %>%
  add_markers(
    data = air, x = ~long, y = ~lat, text = ~airport,
    size = ~cnt, hoverinfo = "text", alpha = 0.5
  ) %>%
  add_segments(
    data = group_by(flights, id),
    x = ~start_lon, xend = ~end_lon,
    y = ~start_lat, yend = ~end_lat,
    alpha = 0.3, size = I(1), hoverinfo = "none"
  ) %>%
  layout(
    title = 'Feb. 2011 American Airline flight paths<br>(Hover for airport names)',
    geo = geo, showlegend = FALSE, height=800
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="map-flights")
chart_link
```

```{r, echo=FALSE, height=800}
chart_link
```

### London to NYC Great Circle

```{r, results = 'hide'}
library(plotly)

p <- plot_geo(lat = c(40.7127, 51.5072), lon = c(-74.0059, 0.1275)) %>%
  add_lines(color = I("blue"), size = I(2)) %>%
  layout(
    title = 'London to NYC Great Circle',
    showlegend = FALSE,
    geo = list(
      resolution = 50,
      showland = TRUE,
      showlakes = TRUE,
      landcolor = toRGB("grey80"),
      countrycolor = toRGB("grey80"),
      lakecolor = toRGB("white"),
      projection = list(type = "equirectangular"),
      coastlinewidth = 2,
      lataxis = list(
        range = c(20, 60),
        showgrid = TRUE,
        tickmode = "linear",
        dtick = 10
      ),
      lonaxis = list(
        range = c(-100, 20),
        showgrid = TRUE,
        tickmode = "linear",
        dtick = 20
      )
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="map-london")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Contour lines on globe

```{r, message=FALSE, height=800}
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/globe_contours.csv')
df$id <- seq_len(nrow(df))

library(tidyr)
d <- df %>%
  gather(key, value, -id) %>%
  separate(key, c("l", "line"), "\\.") %>%
  spread(l, value)

geo <- list(
  showland = TRUE,
  showlakes = TRUE,
  showcountries = TRUE,
  showocean = TRUE,
  countrywidth = 0.5,
  landcolor = toRGB("grey90"),
  lakecolor = toRGB("white"),
  oceancolor = toRGB("white"),
  projection = list(
    type = 'orthographic',
    rotation = list(
      lon = -100,
      lat = 40,
      roll = 0
    )
  ),
  lonaxis = list(
    showgrid = TRUE,
    gridcolor = toRGB("gray40"),
    gridwidth = 0.5
  ),
  lataxis = list(
    showgrid = TRUE,
    gridcolor = toRGB("gray40"),
    gridwidth = 0.5
  )
)

p <- plot_geo(d) %>%
  group_by(line) %>%
  add_lines(x = ~lon, y = ~lat) %>%
  layout(
    showlegend = FALSE, geo = geo,
    title = 'Contour lines over globe<br>(Click and drag to rotate)'
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="map-contour")
chart_link
```

```{r, echo=FALSE}
chart_link
```
