---
title: Simple Features in R | Examples | Plotly
name: Simple Features
permalink: r/maps-sf/
description: How to make maps with Plotly and simple features.
layout: base
thumbnail: thumbnail/sf.jpg
language: r
has_thumbnail: true
display_as: maps
order: 7
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Introduction

In order to complete the examples below, you'll require installing additional packages (`install.packages("packageName")`):
- [sf](https://github.com/r-spatial/sf)

The examples below use the library [simple features](https://r-spatial.github.io/sf/) to read in the shape files before plotting the features with Plotly.

### Basic sf 

``` {r, results = 'hide'}
library(plotly)
library(sf)

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)

p <- plot_ly(nc)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="sf-1")
chart_link
```

```{r, echo=FALSE}
chart_link
```

You can also use `plot_geo`:

``` {r, results = 'hide'}
library(plotly)
library(sf)

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)

p <- plot_geo(nc)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="sf-geo")
chart_link
```

```{r, echo=FALSE}
chart_link
```

Or `plot_mapbox`:

``` {r, results = 'hide'}
library(plotly)
library(sf)

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)

p <- plot_mapbox(nc, split=~NAME) %>%
  layout(
    mapbox = list(
      zoom = 6
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="sf-mapbox")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Using ggplot2

Alternatively, if working in ggplot2 you can use [`ggplotly`](https://plot.ly/ggplot2/maps-sf/).

### Reference

See [https://plot.ly/r/reference/](https://plot.ly/r/reference/) for more information and chart attribute options! If you would like to read more on visualizing geo-spatial data with sf and plotly click [here](https://blog.cpsievert.me/2018/03/30/visualizing-geo-spatial-data-with-sf-and-plotly/).
