---
name: Filled Area in Mapbox
permalink: r/filled-area-on-mapbox/
description: How to make an area on Map in R with plotly.
layout: base
thumbnail: thumbnail/area.jpg
language: r
page_type: example_index
display_as: maps
order: 6
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

```{r, echo = FALSE}
# Mapbox token for plotly | this one is for plot_mapbox figure
mapboxToken <- paste("pk.eyJ1IjoicGxvdGx5bWFwYm94IiwiYSI6ImNqdnBvNDMyaT",
                "AxYzkzeW5ubWdpZ2VjbmMifQ.TXcBE-xg9BFdV2ocecc_7g", sep = "")

# Setting mapbox token for R environment 
Sys.setenv("MAPBOX_TOKEN" = mapboxToken)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Mapbox Access Token

To plot on Mapbox maps with Plotly you `may` need a Mapbox account and a public [Mapbox Access Token](https://www.mapbox.com/studio), that you can add to your [Plotly Settings](https://plot.ly/settings/mapbox). See our [Mapbox Map Layers](/python/mapbox-layers/) documentation for more information. If you're using a Chart Studio Enterprise server, please see additional instructions [here](https://help.plot.ly/mapbox-atlas).

### How to Show an Area on a Map

There are three different ways to show an area in a mapbox:
<ol>
    <li> Use [Scattermapbox](https://plot.ly/r/reference/#scattermapbox) trace and set [fill](https://plot.ly/r/reference/#scattermapbox-fill) attribute to 'toself'</li>
    <li> Use [Scattermapbox](https://plot.ly/r/reference/#scattermapbox) trace and define the corresponding geojson</li>
    <li> Use the new trace type: [Choroplethmapbox](https://plot.ly/r/mapbox-county-choropleth/) for mapbox cases, or [Choropleth](https://plot.ly/r/choropleth-maps/) trace for non-mapbox ones.</li>
</ol>
The following example uses `Scattermapbox` and sets `fill = 'toself'`

```{r}
library(plotly)

p <- plot_ly(
  fill = "toself",
  lon = c(-74, -70, -70, -74),
  lat = c(47, 47, 45, 45),
  type = 'scattermapbox',
  marker = list(size = 10, color = 'orange'),
  fillcolor = 'color') %>%
  layout(
    mapbox = list(
      style = "stamen-terrain",
      center = list(lon = -73, lat = 46),
      zoom = 5),
    showlegend = FALSE)

p
```

### Provide Gaps on Map

The following example shows how to use missing values in your data to provide gap in your graph. To ignore the gap on your plot, take benefit of [connectorgaps](https://plot.ly/r/reference/#scattermapbox-connectgaps) attribute.

```{r}
library(plotly)

p <- plot_ly(
  mode = "lines",
  fill = "toself",
  type = 'scattermapbox',
  lon = c(-10, -10, 8, 8, NaN, 30, 30, 50, 50, NaN, 100, 100, 80, 80),
  lat = c(30, 6, 6, 30, NaN, 20, 30, 30, 20, NaN, 40, 50, 50, 40)) %>%
layout(
  mapbox = list(
    style = "stamen-terrain",
    center = list(lon = 30, lat = 30),
    zoom = 2),
  showlegend = FALSE)

p
```


### Use the Corresponding Geojson

The second way is using Scattermapbox trace with the corresponding geojson.

```{r}
library(plotly)

p <- plot_ly(
  type = 'scattermapbox',
  mode = "markers",
  lon = c(-73.605), lat = c(45.51),
  marker = list(size = 20, color = c("cyan"))) %>%
  layout(
    mapbox = list(
    style = "stamen-terrain",
    center = list(lon = -73.6, lat = 45.5),
    zoom = 12,
    layers = list(list(
    source = list(
      type = "FeatureCollection",
      features = list(list(
        type = "Feature",
        geometry = list(
          type = "MultiPolygon",
          coordinates = list(list(list(
            c(-73.606352888, 45.507489991), c(-73.606133883, 45.50687600),
            c(-73.605905904, 45.506773980), c(-73.603533905, 45.505698946),
            c(-73.602475870, 45.506856969), c(-73.600031904, 45.505696003),
            c(-73.599379992, 45.505389066), c(-73.599119902, 45.505632008),
            c(-73.598896977, 45.505514039), c(-73.598783894, 45.505617001),
            c(-73.591308727, 45.516246185), c(-73.591380782, 45.516280145),
            c(-73.596778656, 45.518690062), c(-73.602796770, 45.521348046),
            c(-73.612239983, 45.525564037), c(-73.612422919, 45.525642061),
            c(-73.617229085, 45.527751983), c(-73.617279234, 45.527774160),
            c(-73.617304713, 45.527741334), c(-73.617492052, 45.527498362),
            c(-73.617533258, 45.527512253), c(-73.618074188, 45.526759105),
            c(-73.618271651, 45.526500673), c(-73.618446320, 45.526287943),
            c(-73.618968507, 45.525698560), c(-73.619388002, 45.525216750),
            c(-73.619532966, 45.525064183), c(-73.619686662, 45.524889290),
            c(-73.619787038, 45.524770086), c(-73.619925742, 45.524584939),
            c(-73.619954486, 45.524557690), c(-73.620122362, 45.524377961),
            c(-73.620201713, 45.524298907), c(-73.620775593, 45.523650879)
            )))
            )
          ))
        ),
      type = "fill", below = "traces", color = "royalblue"))))

p
```

#Reference

See [https://plot.ly/r/reference/#scattermapbox](https://plot.ly/r/reference/#scattermapbox) for more information and options!
