---
description: How to make Mapbox maps in R with various base layers, with or without
  needing a Mapbox Access token.
display_as: maps
language: r
layout: base
name: Mapbox Layers
order: 6
output:
  html_document:
    keep_md: true
page_type: example_index
permalink: r/mapbox-layers/
thumbnail: thumbnail/mapbox-layers.png
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Mapbox Access Token

To create mapbox maps with Plotly, you'll need a Mapbox account and a [Mapbox Access Token](https://www.mapbox.com/studio/) that you can add to your [Plotly Settings](https://plot.ly/settings/mapbox). If you're using a Chart Studio Enterprise server, please see additional instructions here: https://help.plot.ly/mapbox-atlas/.

```{r, results = 'hide'}
library(plotly)
Sys.setenv('MAPBOX_TOKEN' = 'your_mapbox_token_here')
```

```{r, echo = FALSE}
# Mapbox token for plotly | this one is for plot_mapbox figure
mapboxToken <- paste("pk.eyJ1IjoicGxvdGx5bWFwYm94IiwiYSI6ImNqdnBvNDMyaT",
                "AxYzkzeW5ubWdpZ2VjbmMifQ.TXcBE-xg9BFdV2ocecc_7g", sep = "")

# Setting mapbox token for R environment 
Sys.setenv("MAPBOX_TOKEN" = mapboxToken)
```

### How Layers work in Mapbox Maps

  If your figure contains one or more traces of type `Scattermapbox`, `Choroplethmapbox` or `Densitymapbox`, the `layout` object in your figure contains configuration information for the map itself. The map is composed of various layers, of three different types.
    <ol>
        <li> `layout.mapbox.style` defines the lowest layers, also known as your "base map"</li>
        <li> The various traces in `data` are by default rendered above the base map (although this can be controlled via the `below` attribute).</li>
        <li> `layout.mapbox.layers` is an array that defines more layers that are by default rendered above the traces in `data` (although this can also be controlled via the `below` attribute).</li>
    </ol>


### Mapbox Access Tokens and When You Need Them

  The word "mapbox" in the trace names and `layout.mapbox` refers to the Mapbox.js open-source library. If your basemap in `layout.mapbox.style` uses data from the Mapbox *service*, then you will need to register for a free account at https://mapbox.com/ and obtain a Mapbox Access token. This token should be provided either in `mapboxAccessToken`  in `setPlotConfig` function, or as a variable that would be passed as an argument of `newPlot`.
    If your `layout.mapbox.style` does not use data from the Mapbox service, you do *not* need to register for a Mapbox account.
    <h6>Base Maps in `layout.mapbox.style`</h6>
    The accepted values for `layout.mapbox.style` are one of the following tiles.
    <ol>
        <li> `"white-bg"` yields an empty white canvas which results in no external HTTP requests </li>
        <li> `"open-street-map"`, `"carto-positron"`, `"carto-darkmatter"`, `"stamen-terrain"`, `"stamen-toner"` or `"stamen-watercolor"` yeild maps composed of *raster* tiles from various public tile servers which do not require signups or access tokens </li>
        <li> `"basic"`, `"streets"`, `"outdoors"`, `"light"`, `"dark"`, `"satellite"`, or `"satellite-streets"` yeild maps composed of *vector* tiles from the Mapbox service, and *do* require a Mapbox Access Token or an on-premise Mapbox installation. </li>
        <li> A Mapbox service style URL, which requires a Mapbox Access Token or an on-premise Mapbox installation. </li>
        <li> A Mapbox Style object as defined at https://docs.mapbox.com/mapbox-gl-js/style-spec/ </li>
    </ol>

### OpenStreetMap Tiles, no Token Needed

   Here is a simple map rendered with "open-street-map" tiles, without needing a Mapbox Access Token.

```{r}
library(plotly)

us_cities = read.csv("https://raw.githubusercontent.com/plotly/datasets/master/us-cities-top-1k.csv")

p <- us_cities %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    marker = list(color = "fuchsia"),
    type = 'scattermapbox',
    hovertext = us_cities[,"City"]) %>%
  layout(
    mapbox = list(
      style = 'open-street-map',
      zoom =2.5,
      center = list(lon = -88, lat = 34)))

p
```

### Using `layout.mapbox.layers` to Specify a Base Map

If you have access to your own private tile servers, or wish to use a tile server not included in the list above, the recommended approach is to set `layout.mapbox.style` to `"white-bg"` and to use `layout.mapbox.layers` with `below` to specify a custom base map.

> If you omit the `below` attribute when using this approach, your data will likely be hidden by fully-opaque raster tiles!

### Base Tiles from the USGS: no Token Needed

Here is an example of a map which uses a public USGS imagery map, specified in `layout.mapbox.layers`, and which is rendered *below* the `data` layer.

```{r}
library(plotly)

us_cities = read.csv("https://raw.githubusercontent.com/plotly/datasets/master/us-cities-top-1k.csv")

p <-  us_cities %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    type = "scattermapbox",
    hovertext = us_cities[,"City"],
    marker = list(color = "fuchsia")) %>%
  layout(mapbox= list(
    style = "white-bg",
    zoom = 3,
    center = list(lon = -93 ,lat= 41),
    layers = list(list(
      below = 'traces',
      sourcetype = "raster",
      source = list("https://basemap.nationalmap.gov/arcgis/rest/services/USGSImageryOnly/MapServer/tile/{z}/{y}/{x}")))))

p
```

#### Base Tiles from the USGS, Radar Overlay from Environment Canada: no Token Needed

Here is the same example, with in addition, a WMS layer from Environment Canada which displays near-real-time radar imagery in partly-transparent raster tiles, rendered above the `go.Scattermapbox` trace, as is the default:

```{r}
library(plotly)
p <- us_cities %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    type = "scattermapbox",
    hovertext = us_cities[,"City"],
    marker = list(color = "fuchsia")) %>%
  layout(
    mapbox= list(
      style = "white-bg",
      sourcetype = 'raster',
      zoom = 3,
      center = list(lon = -93 ,lat= 41),
      layers = list(list(
        below = 'traces',
        sourcetype = "raster",
        source = list("https://basemap.nationalmap.gov/arcgis/rest/services/USGSImageryOnly/MapServer/tile/{z}/{y}/{x}")),
        list(
          sourcetype = "raster",
          source = list("https://geo.weather.gc.ca/geomet/?SERVICE=WMS&VERSION=1.3.0&REQUEST=GetMap&BBOX={bbox-epsg-3857}&CRS=EPSG:3857&WIDTH=1000&HEIGHT=1000&LAYERS=RADAR_1KM_RDBR&TILED=true&FORMAT=image/png")))))

p
```

#### Dark Tiles from Mapbox Service: Free Token Needed

Here is a map rendered with the `"dark"` style from the Mapbox service, which requires an Access Token:

```{r}
library(plotly)

#mapboxToken <- paste(readLines(".mapbox_token"), collapse="")    # You need your own token

us_cities = read.csv("https://raw.githubusercontent.com/plotly/datasets/master/us-cities-top-1k.csv")

p <- us_cities %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    marker = list(color = "fuchsia"),
    type = 'scattermapbox',
    hovertext = us_cities[,"City"]) %>%
  layout(
    mapbox = list(
      style = 'dark',
      accesstoken = mapboxToken,
      zoom =2.5,
      center = list(lon = -88, lat = 34)))

p
```

#Reference

See [https://plot.ly/r/reference/#scattermapbox](https://plot.ly/r/reference/#scattermapbox) for more information and options!