---
name: Setting Graph Size
permalink: r/setting-graph-size/
description: How to change the size of graphs in R.
layout: base
language: r
page_type: example_index
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Customize Margins and Plot Size
```{r}
library(plotly)
m <- list(
  l = 50,
  r = 50,
  b = 100,
  t = 100,
  pad = 4
)
p <- plot_ly(x = seq(0, 8), y = seq(0, 8)) %>%
  layout(autosize = F, width = 500, height = 500, margin = m)

p
```

### Automatically Adjust Margins
```{r}
library(plotly)
yaxis <- list(
  title = 'Y-axis Title',
  ticktext = list('long label','Very long label','3','label'),
  tickvals = list(1, 2, 3, 4),
  tickmode = "array",
  automargin = TRUE,
  titlefont = list(size=30)
)
p <- plot_ly(x = c('Apples', 'Oranges', 'Watermelon', 'Pears'), y = c(3, 1, 2, 4), width = 500, height = 500, type = 'bar') %>%
  layout(autosize = F, yaxis = yaxis)

p
```
