---
title: Axes Labels in R
name: Axes Labels
permalink: r/figure-labels/
description: How to set the title and axis-titles in R
layout: base
thumbnail: figure-labels.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Figure Labels for 2D Charts
```{r, results = 'hide'}
library(plotly)
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "x Axis",
  titlefont = f
)
y <- list(
  title = "y Axis",
  titlefont = f
)
p <- plot_ly(x = ~rnorm(10), y = ~rnorm(10), mode = "markers") %>%
  layout(xaxis = x, yaxis = y)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="scatter2d-axis-labels")
chart_link
```

```{r, results='asis', echo=FALSE}
chart_link
```

#### Figure Labels for 3D Charts

```{r, results = 'hide'}
library(plotly)
set.seed(123)

n <- 100
theta <- runif(n, 0, 2*pi)
u <- runif(n, -1, 1)

p <- plot_ly(x = ~sqrt(1 - u^2) * cos(theta), y = ~sqrt(1 - u^2) * sin(theta), z = ~u) %>%
  layout(
    title = "Layout options in a 3d scatter plot",
    scene = list(
      xaxis = list(title = "Cos"),
      yaxis = list(title = "Sin"),
      zaxis = list(title = "Z")
    ))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="scatter3d-axis-labels")
chart_link
```

```{r, results='asis', echo=FALSE}
chart_link
```
