---
title: Legends in R | Examples | Plotly
name: Legends
permalink: r/legend/
description: How to modify the legend in R graphs. Nine examples of how to move, color, and hide the legend.
layout: base
thumbnail: thumbnail/legends.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Legend Names

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3') %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5')

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-names")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Hiding the Legend

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~Tree2) %>%
  add_trace(y = ~Tree3) %>%
  add_trace(y = ~Tree4) %>%
  add_trace(y = ~Tree5) %>%
  layout(showlegend = FALSE)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-hiding")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Hiding Legend Entries

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3', showlegend = FALSE) %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5')

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-hiding2")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Positioning the Legend Inside the Plot

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3') %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5') %>%
  layout(legend = list(x = 0.1, y = 0.9))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-position_in")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Positioning the Legend Outside the Plot

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3') %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5') %>%
  layout(legend = list(x = 100, y = 0.5))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-position_out")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Changing the Legend Orientation

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3') %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5') %>%
  layout(legend = list(orientation = 'h'))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-orientation")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Styling the Legend

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

l <- list(
  font = list(
    family = "sans-serif",
    size = 12,
    color = "#000"),
  bgcolor = "#E2E2E2",
  bordercolor = "#FFFFFF",
  borderwidth = 2)


p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', name = 'Tree 1') %>%
  add_trace(y = ~Tree2, name = 'Tree 2') %>%
  add_trace(y = ~Tree3, name = 'Tree 3') %>%
  add_trace(y = ~Tree4, name = 'Tree 4') %>%
  add_trace(y = ~Tree5, name = 'Tree 5') %>%
  layout(legend = l)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-style")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Grouped Legend

Plotly legends are interactive. Click on the legend entries to hide and show traces. The legendgroup key groups legend entries so that clicking on one legend entry will hide or show all of the traces in that group.

```{r, results = 'hide'}
library(plotly)
library(tidyr)
library(plyr)

data <- spread(Orange, Tree, circumference)
data <- rename(data, c("1" = "Tree1", "2" = "Tree2", "3" = "Tree3", "4" = "Tree4", "5" = "Tree5"))

p <- plot_ly(data, x = ~age, y = ~Tree1, type = 'scatter', mode = 'lines', 
        legendgroup = 'group1', name = 'Zone 1 - Tree 1') %>%
  add_trace(y = ~Tree2, legendgroup = 'group2', name = 'Zone 2 - Tree 1') %>%
  add_trace(y = ~Tree3, legendgroup = 'group1', name = 'Zone 1 - Tree 2') %>%
  add_trace(y = ~Tree4, legendgroup = 'group2', name = 'Zone 2 - Tree 2') %>%
  add_trace(y = ~Tree5, legendgroup = 'group1', name = 'Zone 1 - Tree 3') 

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-grouped")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Subplot Grouped Legend

```{r, results = 'hide'}
library(plotly)

df <- data.frame(x = c("a","b","c"), y = c(2,3,2), y2 = c(4,2,4))

p1 <- df %>%
  plot_ly(
    type = 'bar', 
    x = ~x, 
    y = ~y, 
    color = ~x, 
    legendgroup = ~x
  ) %>% 
  layout(
    xaxis = list(
      showgrid = F
    ),
    yaxis = list(
      showgrid = F
    )
  )

p2 <- df%>% 
  plot_ly(
    type = 'bar', 
    x = ~x, 
    y = ~y2, 
    color =  ~x, 
    legendgroup = ~x, 
    showlegend = F
  ) %>% 
  layout(
    xaxis = list(
      showgrid = F
    ),
    yaxis = list(
      showgrid = F
    )
  )

p <- subplot(p1, p2, nrows = 2, shareX = T) 

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="legend-subplot-grouped")
chart_link
```

```{r, echo=FALSE}
chart_link
```

Reference

See [https://plot.ly/r/reference/#layout-legend](https://plot.ly/r/reference/#layout-legend) for more information and chart attribute options!


