---
title: Modifying 3D Axes in R | Examples | Plotly
name: 3D Axes
permalink: r/3d-axes/
description: How to format axes of 3d plots in R with Plotly.
layout: base
thumbnail: thumbnail/your-tutorial-chart.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Range of Axes

```{r, results = 'hide'}
library(plotly)

axx <- list(
  nticks = 4,
  range = c(-25,75)
)

axy <- list(
  nticks = 4,
  range = c(-25,75)
)

axz <- list(
  nticks = 4,
  range = c(0,50)
)

x <- 70*(runif(70, 0, 1))
y <- 55*(runif(70, 0, 1))
z <- 40*(runif(70, 0, 1))

p <- plot_ly(x = ~x, y = ~y, z = ~z, type = 'mesh3d') %>%
  layout(scene = list(xaxis=axx,yaxis=axy,zaxis=axz))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="axes3d-range")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Set Axes Title

```{r, results = 'hide'}
library(plotly)

axx <- list(
  title = "X AXIS TITLE"
)

axy <- list(
  title = "Y AXIS TITLE"
)

axz <- list(
  title = "Z AXIS TITLE"
)

x <- 70*(runif(70, 0, 1))
y <- 55*(runif(70, 0, 1))
z <- 40*(runif(70, 0, 1))

p <- plot_ly(x = ~x, y = ~y, z = ~z, type = 'mesh3d') %>%
  layout(scene = list(xaxis=axx,yaxis=axy,zaxis=axz))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="axes3d-title")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Ticks Formatting

```{r, results = 'hide'}
library(plotly)

axx <- list(
  ticketmode = 'array',
  ticktext = c("Huey", "Dewey", "Louie"),
  tickvals = c(0,25,50),
  range = c(-25,75)
)

axy <- list(
  nticks = 4,
  range = c(-25,75)
)

axz <- list(
  nticks = 4,
  range = c(0,50)
)

x <- 70*(runif(70, 0, 1))
y <- 55*(runif(70, 0, 1))
z <- 40*(runif(70, 0, 1))

p <- plot_ly(x = ~x, y = ~y, z = ~z, type = 'mesh3d') %>%
  layout(scene = list(xaxis=axx,yaxis=axy,zaxis=axz))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="axes3d-ticks")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Background and Grid Color

```{r, results = 'hide'}
library(plotly)

axx <- list(
  backgroundcolor="rgb(200, 200, 230",
  gridcolor="rgb(255,255,255)",
  showbackground=TRUE,
  zerolinecolor="rgb(255,255,255"
)

axy <- list(
  backgroundcolor="rgb(230, 200,230)",
  gridcolor="rgb(255,255,255)",
  showbackground=TRUE,
  zerolinecolor="rgb(255,255,255"
)

axz <- list(
  backgroundcolor="rgb(230, 230,200)",
  gridcolor="rgb(255,255,255)",
  showbackground=TRUE,
  zerolinecolor="rgb(255,255,255"
)

x <- 70*(runif(70, 0, 1))
y <- 55*(runif(70, 0, 1))
z <- 40*(runif(70, 0, 1))

p <- plot_ly(x = ~x, y = ~y, z = ~z, type = 'mesh3d') %>%
  layout(scene = list(xaxis=axx,yaxis=axy,zaxis=axz))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="axes3d-bg-grid")
chart_link
```

```{r, echo=FALSE}
chart_link
```

#Reference

See [https://plot.ly/r/reference/#layout-scene-xaxis](https://plot.ly/r/reference/#layout-scene-xaxis) for more information and options!

