---
name: 3D Surface Lighting in R
permalink: r/3d-surface-lighting/
description: How to add lighting effects in 3D R Plots.
layout: base
thumbnail: thumbnail/your-tutorial-chart.jpg
language: r
page_type: example_index
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Ambient

```{r}
p1 <- plot_ly(z = ~volcano, scene='scene1', lighting = list(ambient = 0.2)) %>%
  add_surface(showscale=FALSE)

p2 <- plot_ly(z = ~volcano, scene='scene2', lighting = list(ambient = 0.9)) %>%
  add_surface(showscale=FALSE)

p <- subplot(p1, p2) %>%
  layout(title = "Ambient Lighting",
         grid = list(rows = 1, columns = 2,
                     pattern = 'independent'),
         scene = list(domain=list(column = 0),
                      aspectmode='cube'),
         scene2 = list(domain=list(column = 1),
                       aspectmode='cube'))

p
```

### Roughness

```{r}
p1 <- plot_ly(z = ~volcano, scene='scene1', lighting = list(roughness = 0.1)) %>%
  add_surface(showscale=FALSE)

p2 <- plot_ly(z = ~volcano, scene='scene2', lighting = list(roughness = 0.9)) %>%
  add_surface(showscale=FALSE)

p <- subplot(p1, p2) %>%
  layout(title = "Roughness",
         grid = list(rows = 1, columns = 2,
                     pattern = 'independent'),
         scene = list(domain=list(column = 0),
                      aspectmode='cube'),
         scene2 = list(domain=list(column = 1),
                       aspectmode='cube'))

p
```

### Diffuse

```{r}
p1 <- plot_ly(z = ~volcano, scene='scene1', lighting = list(diffuse = 0.1)) %>%
  add_surface(showscale=FALSE)

p2 <- plot_ly(z = ~volcano, scene='scene2', lighting = list(diffuse = 0.9)) %>%
  add_surface(showscale=FALSE)

p <- subplot(p1, p2) %>%
  layout(title = "Diffuse Reflection",
         grid = list(rows = 1, columns = 2,
                     pattern = 'independent'),
         scene = list(domain=list(column = 0),
                      aspectmode='cube'),
         scene2 = list(domain=list(column = 1),
                       aspectmode='cube'))

p
```

### Specular

```{r}
p1 <- plot_ly(z = ~volcano, scene='scene1', lighting = list(specular = 0.1)) %>%
  add_surface(showscale=FALSE)

p2 <- plot_ly(z = ~volcano, scene='scene2', lighting = list(specular = 1.9)) %>%
  add_surface(showscale=FALSE)

p <- subplot(p1, p2) %>%
  layout(title = "Specular Reflection",
         grid = list(rows = 1, columns = 2,
                     pattern = 'independent'),
         scene = list(domain=list(column = 0),
                      aspectmode='cube'),
         scene2 = list(domain=list(column = 1),
                       aspectmode='cube'))

p
```

### Fresnel

```{r}
p1 <- plot_ly(z = ~volcano, scene='scene1', lighting = list(fresnel = 0.1)) %>%
  add_surface(showscale=FALSE)

p2 <- plot_ly(z = ~volcano, scene='scene2', lighting = list(fresnel = 4.5)) %>%
  add_surface(showscale=FALSE)

p <- subplot(p1, p2) %>%
  layout(title = "Fresnel",
         grid = list(rows = 1, columns = 2,
                     pattern = 'independent'),
         scene = list(domain=list(column = 0),
                      aspectmode='cube'),
         scene2 = list(domain=list(column = 1),
                       aspectmode='cube'))

p
```

#Reference

See [https://plot.ly/r/reference/#surface-lighting](https://plot.ly/r/reference/#surface-lighting) for more information and options!

