---
name: Hover Text and Formatting
permalink: r/hover-text-and-formatting/
description: How to use hover text and formatting in R with Plotly.
layout: base
thumbnail: thumbnail/hover'text.jpg
language: r
display_as: layout_opt
page_type: example_index
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

#### Add Hover Text

```{r}
library(plotly)

p <- plot_ly(type = 'scatter', mode = 'markers') %>%
  add_trace(
    x = c(1:5), 
    y = rnorm(5, mean = 5),
    text = c("Text A", "Text B", "Text C", "Text D", "Text E"),
    hoverinfo = 'text',
    marker = list(color='green'),
    showlegend = F
  )

p
```

#### Format Hover Text 

```{r}
library(plotly)

p <- plot_ly(type = 'scatter', mode = 'markers') %>%
  add_trace(
    x = c(1:100), 
    y = rnorm(100, mean = 5), 
    marker = list(color='green'),
    hoverinfo = 'y',
    showlegend = F
  ) %>%
  layout(
    title = "Set hover text formatting<br><a href= https://github.com/d3/d3-time-format/blob/master/README.md#locale_format>https://github.com/d3/d3-time-format/blob/master/README.md#locale_format</a>",
    titlefont = list(
      size = 10
    ),
    xaxis = list(
      zeroline = F
    ),
    yaxis = list(
      hoverformat = '.2f'
    )
  )

p
```

#### Hovertemplate

```{r}
library(plotly)

p <- plot_ly() %>%
  add_trace(
    type = 'scatter',
    mode = 'lines+markers',
    x = c(1,2,3,4,5),
    y = c(2.02825,1.63728,6.83839,4.8485,4.73463),
    text = c("Text A", "Text B", "Text C", "Text D", "Text E"),
    hovertemplate = paste('<i>Price</i>: $%{y:.2f}',
                        '<br><b>X</b>: %{x}<br>',
                        '<b>%{text}</b>'),
    showlegend = FALSE
  ) %>%
  add_trace(
    type = 'scatter',
    mode = 'lines+markers',
    x = c(1,2,3,4,5),
    y = c(3.02825,2.63728,4.83839,3.8485,1.73463),
    hovertemplate = 'Price: %{y:$.2f}<extra></extra>',
    showlegend = FALSE
  )

p
```

#### Advanced Hovertemplate

```{r}
library(plotly)

d <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/job-automation-probability.csv')

p <- d %>% 
  plot_ly(
    type = 'scatter',
    mode = 'markers',
    x = ~prob,
    y = ~Average.annual.wage,
    marker = list(size = ~numbEmployed, sizeref = 4000, sizemode = 'area'),
    color = ~education,
    text = ~short.occupation,
    hovertemplate = paste(
      "<b>%{text}</b><br><br>",
      "%{yaxis.title.text}: %{y:$,.0f}<br>",
      "%{xaxis.title.text}: %{x:.0%}<br>",
      "Number Employed: %{marker.size:,}",
      "<extra></extra>"
      )
    ) %>%
  layout(legend = list(orientation = 'h', y = -0.3))

p
```

#### Reference

See [https://plot.ly/r/reference/](https://plot.ly/r/reference/) for more information and options!
