---
title: Coupled hover events with Shiny and Plotly | Examples | Plotly
name: Coupled hover events with Shiny and Plotly
permalink: r/shiny-coupled-hover-events/
redirect_from:
  - ggplot2/shiny-tutorial/
  - r/shiny/
  - ggplot2/shiny/
description: Coupled events with Shiny and Plotly
layout: base
language: r
page_type: example_index
has_thumbnail: false
display_as: get_request
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Coupled Hover Events in Plotly using Shiny
Apart from **click** and **selection** events, Plotly supports **hover** events as well.

- `plotly_hover` can be used to return information about data points on mouse hover.

Below is an example on how to couple a hover event on one chart to trigger a computation on another chart. For an example showcasing **click** and **selection** events see [here](/r/shiny-coupled-events/)

### UI

```{r, results = 'hide'}
library(shiny)
library(plotly)
library(shinythemes)
library(dplyr)

ui <- fluidPage(
  # Set theme
  theme = shinytheme("spacelab"),
  
  # Some help text
  h2("Coupled hover-events in plotly charts using Shiny"),
  h4("This Shiny app showcases coupled hover-events using Plotly's ", tags$code("event_data()"), " function."),
  
  # Vertical space
  tags$hr(),
  
  # Window length selector
  selectInput("window", label = "Select Window Length", choices = c(10, 20, 30, 60, 90), selected = 10),
  
  # Plotly Chart Area
  fluidRow(
    column(6, plotlyOutput(outputId = "timeseries", height = "600px")),
    column(6, plotlyOutput(outputId = "correlation", height = "600px"))),
  
  tags$hr(),
  tags$blockquote("Hover over time series chart to fix a specific date. Correlation chart will update with historical 
                  correlations (time span will be hover date +/- selected window length)")
  )
```

### Server

```{r, results = 'hide'}
server <- function(input, output){
  
  # Read data
  stockdata <- read.csv("https://cdn.rawgit.com/plotly/datasets/master/stockdata.csv")
  
  # Create dates
  stockdata$Date <- as.Date(stockdata$Date)
  
  # Reshape
  ds <- reshape2::melt(stockdata, id = "Date")
  ds <- filter(ds, variable != "GSPC")
  
  # Set some colors
  plotcolor <- "#F5F1DA"
  papercolor <- "#E3DFC8"
  
  # Plot time series chart 
  output$timeseries <- renderPlotly({
    p <- plot_ly(source = "source") %>% 
      add_lines(data = ds, x = ~Date, y = ~value, color = ~variable, mode = "lines", line = list(width = 3))
    
    # Add SP500
    p <- p %>%
      add_lines(data = stockdata, x = ~Date, y = ~GSPC, mode = "lines", yaxis = "y2", name = "SP500", opacity = 0.3,
                   line = list(width = 5)) %>% 
      layout(title = "Stock prices for different stocks overlaid with SP500",
             xaxis = list(title = "Dates", gridcolor = "#bfbfbf", domain = c(0, 0.98)),
             yaxis = list(title = "Stock Price", gridcolor = "#bfbfbf"), 
             plot_bgcolor = plotcolor,
             paper_bgcolor = papercolor, 
             yaxis2 = list(title = "SP500", side = "right", overlaying = "y"))
    p
  })
  
  # Coupled hover event
  output$correlation <- renderPlotly({
    
    # Read in hover data
    eventdata <- event_data("plotly_hover", source = "source")
    validate(need(!is.null(eventdata), "Hover over the time series chart to populate this heatmap"))
    
    # Get point number
    datapoint <- as.numeric(eventdata$pointNumber)[1]
    
    # Get window length
    window <- as.numeric(input$window)
    
    # Show correlation heatmap
    rng <- (datapoint - window):(datapoint + window)
    cormat <- round(cor(stockdata[rng, 1:5]),2)
    
    plot_ly(x = rownames(cormat), y = colnames(cormat), z = cormat, type = "heatmap", 
            colors = colorRamp(c('#e3dfc8', '#808c6c')))%>% 
      layout(title = "Correlation heatmap",
             xaxis = list(title = ""),
             yaxis = list(title = ""))
    
  })
  
}
```

### Shiny app



#Reference

See [https://plot.ly/r/reference](https://plot.ly/r/reference) for more information and chart attribute options!
