---
name: Formatting Ticks
permalink: r/tick-formatting/
description: How to format axes ticks in R.
layout: base
language: r
page_type: example_index
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Tickmode - Linear

```{r}
library(plotly)

p <- plot_ly(
  type = "scatter",
  x = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12), 
  y = c(28.8, 28.5, 37, 56.8, 69.7, 79.7, 78.5, 77.8, 74.1, 62.6, 45.3, 39.9), 
  mode = "markers+lines") %>%
  layout(
    xaxis = list(
      dtick = 0.75, 
      tick0 = 0.5, 
      tickmode = "linear"
  ))

p
```

### Tickmode - Array

```{r}
library(plotly)

p <- plot_ly(
  type = "scatter",
  x = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12), 
  y = c(28.8, 28.5, 37, 56.8, 69.7, 79.7, 78.5, 77.8, 74.1, 62.6, 45.3, 39.9), 
  mode = "markers+lines") %>%
  layout(
    xaxis = list(
      ticktext = list("One", "Three", "Five", "Seven", "Nine", "Eleven"), 
      tickvals = list(1, 3, 5, 7, 9, 11),
      tickmode = "array"
  ))

p
```


### Using Tickformat

```{r}
library(plotly)

p <- plot_ly(
  type = "scatter",
  x = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12), 
  y = c(0.18, 0.38, 0.56, 0.46, 0.59, 0.4, 0.78, 0.77, 0.74, 0.42, 0.45, 0.39), 
  mode = "markers+lines") %>%
  layout(
    yaxis = list(
        tickformat = "%"
  ))

p
```

### Using Tickformat (Date)

```{r}
library(plotly)

df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/finance-charts-apple.csv')

p <- plot_ly(
  type = "scatter",
  x = df$Date, 
  y = df$AAPL.High,
  name = 'AAPL High',
  mode = "lines",
  line = list(
        color = '#17BECF'
  )) %>%
  add_trace(
    type = "scatter",
    x = df$Date, 
    y = df$AAPL.Low,
    name = 'AAPL Low',
    mode = "lines",
    line = list(
        color = '#7F7F7F'
  )) %>%
  layout(
    title = "Time Series with Custom Date-Time Format",
    xaxis = list(
        type = 'date',
        tickformat = "%d %B (%a)<br>%Y"
  ))

p
```

### Tickformatstops to customize for different zoom levels

```{r}
library(plotly)
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/finance-charts-apple.csv')
p <- plot_ly(
  type = "scatter",
  x = df$Date, 
  y = df$mavg,
  mode = "lines") %>%
  layout(
    xaxis = list(
      type='date',
      tickformatstops = list(
        list(
          dtickrange = list(NULL, 1000), 
          value = "%H:%M:%S.%L ms"
        ), 
        list(
          dtickrange = list(1000, 60000), 
          value = "%H:%M:%S s"
        ), 
        list(
          dtickrange = list(60000, 3600000), 
          value = "%H:%M m"
        ), 
        list(
          dtickrange = list(3600000, 86400000), 
          value = "%H:%M h"
        ), 
        list(
          dtickrange = list(86400000, 604800000), 
          value = "%e. %b d"
        ), 
        list(
          dtickrange = list(604800000, "M1"), 
          value = "%e. %b w"
        ), 
        list(
          dtickrange = list("M1", "M12"), 
          value = "%b '%y M"
        ), 
        list(
          dtickrange = list("M12", NULL), 
          value = "%Y Y"
        )
      )
    )
  )

p
```

### Using Exponentformat

```{r}
library(plotly)

p <- plot_ly(
  type = "scatter",
  x = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12), 
  y = c(68000, 52000, 60000, 20000, 95000, 40000, 60000, 79000, 74000, 42000, 20000, 90000),
  mode = "markers+lines") %>%
  layout(
    yaxis = list(
      showexponent = "all",
      exponentformat = "e"
    )
  )

p
```
