---
name: Heatmaps
permalink: r/heatmaps/
description: How to make a heatmap in R with a matrix. Seven examples of colored and labeled heatmaps with custom colorscales.
layout: base
thumbnail: thumbnail/heatmap.jpg
language: r
page_type: example_index
display_as: scientific
order: 7
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Basic Heatmap

```{r}
library(plotly)
p <- plot_ly(z = volcano, type = "heatmap")

p
```


#### Categorical Axes

```{r}
m <- matrix(rnorm(9), nrow = 3, ncol = 3)
p <- plot_ly(
	x = c("a", "b", "c"), y = c("d", "e", "f"),
	z = m, type = "heatmap"
)

p
```

#### Sequential Colorscales: Greys

The `colors` argument understands color brewer palettes (see `RColorBrewer::brewer.pal.info` for valid names).

```{r}
p <- plot_ly(z = volcano, colors = "Greys", type = "heatmap")

p
```

#### Custom colorscales

The `colors` argument also accepts a color interpolation function like `colorRamp()`

```{r}
p <- plot_ly(z = volcano, colors = colorRamp(c("red", "green")), type = "heatmap")

p
```

Or, you can do the scaling yourself and use the colorscale attribute directly...

```{r}
vals <- unique(scales::rescale(c(volcano)))
o <- order(vals, decreasing = FALSE)
cols <- scales::col_numeric("Blues", domain = NULL)(vals)
colz <- setNames(data.frame(vals[o], cols[o]), NULL)
p <- plot_ly(z = volcano, colorscale = colz, type = "heatmap")

p
```

