---
title: Time Series in R | Examples | Plotly
name: Time Series
permalink: r/time-series/
description: How to plot date and time in R. An example of a time series plot with the POSIXct and Sys.Date classes.
layout: base
thumbnail: thumbnail/time-series.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: financial
order: 1
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Dates

```{r, results = 'hide'}
library(plotly)
today <- Sys.Date()
tm <- seq(0, 600, by = 10)
x <- today - tm
y <- rnorm(length(x))
p <- plot_ly(x = ~x, y = ~y, mode = 'lines', text = paste(tm, "days from today"))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="timeseries-1")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### POSIXlt date time class with timezone

```{r, results = 'hide'}
library(plotly)
now_lt <- as.POSIXlt(Sys.time(), tz = "GMT")
tm <- seq(0, 600, by = 10)
x <- now_lt - tm
y <- rnorm(length(x))
p <- plot_ly(x = ~x, y = ~y, mode = 'lines', text = paste(tm, "seconds from now in GMT"))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="timeseries-2")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### POSIXct date time class without timezone

```{r, results = 'hide'}
library(plotly)
now_ct <- as.POSIXct(Sys.time())
tm <- seq(0, 600, by = 10)
x <- now_ct - tm
y <- rnorm(length(x))
p <- plot_ly(x = ~x, y = ~y, mode = 'lines', text = paste(tm, "seconds from now in", Sys.timezone()))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="timeseries-3")
chart_link
```

```{r, echo=FALSE}
chart_link
```
