---
title: Candlestick Charts in R | Examples | Plotly
name: Candlestick Charts
permalink: r/candlestick-charts/
description: How to create candlestick charts in R.
layout: base
thumbnail: thumbnail/candlestick.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: financial
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Candlestick

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

# basic example of ohlc charts
df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 30)

p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low) %>%
  layout(title = "Basic Candlestick Chart")

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Candlestick without Rangeslider

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 30)

p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low) %>%
  layout(title = "Basic Candlestick Chart",
         xaxis = list(rangeslider = list(visible = F)))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-rangeslider")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Customise the Figure with Shapes and Annotations

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

df <- data.frame(Date=index(AAPL),coredata(AAPL))

# annotation
a <- list(text = "Stock Split",
          x = '2014-06-06',
          y = 1.02,
          xref = 'x',
          yref = 'paper',
          xanchor = 'left',
          showarrow = FALSE
)

# use shapes to create a line
l <- list(type = line,
          x0 = '2014-06-06',
          x1 = '2014-06-06',
          y0 = 0,
          y1 = 1,
          xref = 'x',
          yref = 'paper',
          line = list(color = 'black',
                      width = 0.5)
)

p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low) %>%
  layout(title = "Apple Stock",
         annotations = a,
         shapes = l)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-custom")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Custom Candlestick Colors

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

# basic example of ohlc charts
df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 30)

# cutom colors
i <- list(line = list(color = '#FFD700'))
d <- list(line = list(color = '#0000ff'))

p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low,
          increasing = i, decreasing = d)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-colors")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Add a Trace to Candlestick Chart

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 365)

p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low) %>%
  add_lines(x = ~Date, y = ~AAPL.Open, line = list(color = 'black', width = 0.75), inherit = F) %>%
  layout(showlegend = FALSE)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-trace")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Candlestick Using Segments

```{r, results = 'hide'}
library(plotly)
library(quantmod)

msft <- getSymbols("MSFT", auto.assign = F)
dat <- as.data.frame(msft)
dat$date <- index(msft)
dat <- subset(dat, date >= "2016-01-01")

names(dat) <- sub("^MSFT\\.", "", names(dat))

p <- plot_ly(dat, x = ~date, xend = ~date, color = ~Close > Open,
             colors = c("red", "forestgreen"), hoverinfo = "none") %>%
       add_segments(y = ~Low, yend = ~High, size = I(1)) %>%
       add_segments(y = ~Open, yend = ~Close, size = I(3)) %>%
       layout(showlegend = FALSE, yaxis = list(title = "Price")) %>%
       rangeslider()

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-segments")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Add Bollinger Bands and Buttons

```{r, results = 'hide'}
library(plotly)
library(quantmod)

# get data
getSymbols("AAPL",src='yahoo')
df <- data.frame(Date=index(AAPL),coredata(AAPL))

# create Bollinger Bands
bbands <- BBands(AAPL[,c("AAPL.High","AAPL.Low","AAPL.Close")])

# join and subset data
df <- subset(cbind(df, data.frame(bbands[,1:3])), Date >= "2015-02-14")

# colors column for increasing and decreasing
for (i in 1:length(df[,1])) {
  if (df$AAPL.Close[i] >= df$AAPL.Open[i]) {
      df$direction[i] = 'Increasing'
  } else {
      df$direction[i] = 'Decreasing'
  }
}

i <- list(line = list(color = '#17BECF'))
d <- list(line = list(color = '#7F7F7F'))

# plot candlestick chart
p <- df %>%
  plot_ly(x = ~Date, type="candlestick",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low, name = "AAPL",
          increasing = i, decreasing = d) %>%
  add_lines(x = ~Date, y = ~up , name = "B Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands",
            hoverinfo = "none", inherit = F) %>%
  add_lines(x = ~Date, y = ~dn, name = "B Bands",
            line = list(color = '#ccc', width = 0.5),
            legendgroup = "Bollinger Bands", inherit = F,
            showlegend = FALSE, hoverinfo = "none") %>%
  add_lines(x = ~Date, y = ~mavg, name = "Mv Avg",
            line = list(color = '#E377C2', width = 0.5),
            hoverinfo = "none", inherit = F) %>%
  layout(yaxis = list(title = "Price"))

# plot volume bar chart
pp <- df %>%
  plot_ly(x=~Date, y=~AAPL.Volume, type='bar', name = "AAPL Volume",
          color = ~direction, colors = c('#17BECF','#7F7F7F')) %>%
  layout(yaxis = list(title = "Volume"))

# create rangeselector buttons
rs <- list(visible = TRUE, x = 0.5, y = -0.055,
           xanchor = 'center', yref = 'paper',
           font = list(size = 9),
           buttons = list(
             list(count=1,
                  label='RESET',
                  step='all'),
             list(count=1,
                  label='1 YR',
                  step='year',
                  stepmode='backward'),
             list(count=3,
                  label='3 MO',
                  step='month',
                  stepmode='backward'),
             list(count=1,
                  label='1 MO',
                  step='month',
                  stepmode='backward')
           ))

# subplot with shared x axis
p <- subplot(p, pp, heights = c(0.7,0.2), nrows=2,
             shareX = TRUE, titleY = TRUE) %>%
  layout(title = paste("Apple: 2015-02-14 -",Sys.Date()),
         xaxis = list(rangeselector = rs),
         legend = list(orientation = 'h', x = 0.5, y = 1,
                       xanchor = 'center', yref = 'paper',
                       font = list(size = 10),
                       bgcolor = 'transparent'))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="finance-candlestick-bbands")
chart_link
```

```{r, echo=FALSE}
chart_link
```

#Reference

See [https://plot.ly/r/reference](https://plot.ly/r/reference) for more information and chart attribute options!
