---
name: Funnel Charts
permalink: r/funnel-charts/
description: How to create a Funnel Chart in R with Plotly
layout: base
thumbnail: thumbnail/funnel.jpg
language: r
page_type: example_index
display_as: financial
order: 5
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```


```{r, echo=FALSE, message=FALSE, results="hide"}
# Install plotly from github for funnel plot
devtools::install_github("ropensci/plotly")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Introduction
Funnel charts are often used to represent data in different stages of a business process. It’s an important mechanism in Business Intelligence to identify potential problem areas of a process. For example, it’s used to observe the revenue or loss in a sales process for each stage, and displays values that are decreasing progressively. Each stage is illustrated as a percentage of the total of all values.

### Basic Funnel Plot

```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly() %>%
  add_trace(
  type = "funnel",
  y = c("Website visit", "Downloads", "Potential customers", "Requested price", "invoice sent"),
  x = c(39, 27.4, 20.6, 11, 2)) %>%
  layout(yaxis = list(categoryarray = c("Website visit", "Downloads", "Potential customers", "Requested price", "invoice sent")))

p
```


### Setting Marker Size and Color
This example uses [textposition](https://plot.ly/python/reference/#scatter-textposition) and [textinfo](https://plot.ly/python/reference/#funnel-textinfo) to determine information apears on the graph, and shows how to customize the bars.

```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly() %>%
  add_trace(type = "funnel",
            y = c("Website visit", "Downloads", "Potential customers", "Requested price", "Finalized"),
            x = c(39, 27.4, 20.6, 11, 2),
            textposition = "inside",
            textinfo = "value+percent initial",
            opacity = 0.65,
            marker = list(color = c("deepskyblue", "lightsalmon", "tan", "teal", "silver"),
                          line = list(width = c(4, 2, 2, 3, 1, 1), color = c("wheat", "wheat", "blue", "wheat", "wheat"))),
            connector = list(line = list(color = "royalblue", dash = "dot", width = 3))) %>%
  layout(yaxis = list(categoryarray = c("Website visit", "Downloads", "Potential customers", "Requested price", "Finalized")))

p
```

### Stacked Funnel Plot

```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly(
    type = "funnel",
    name = 'Montreal',
    y = c("Website visit", "Downloads", "Potential customers", "Requested price"),
    x = c(120, 60, 30, 20),
    textinfo = "value+percent initial") %>%
  add_trace(
    type = "funnel",
    name = 'Toronto',
    orientation = "h",
    y = c("Website visit", "Downloads", "Potential customers", "Requested price", "invoice sent"),
    x = c(100, 60, 40, 30, 20),
    textposition = "inside",
    textinfo = "value+percent previous") %>%
  add_trace(
    type = "funnel",
    name = 'Vancouver',
    orientation = "h",
    y = c("Website visit", "Downloads", "Potential customers", "Requested price", "invoice sent", "Finalized"),
  x = c(90, 70, 50, 30, 10, 5),
  textposition = "outside",
  textinfo = "value+percent total") %>%
  layout(yaxis = list(categoryarray = c("Website visit", "Downloads", "Potential customers", "Requested price", "invoice sent", "Finalized")))

p
```

### Basic Area Funnel Plot

```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly(
  type = "funnelarea",
  text = c("The 1st","The 2nd", "The 3rd", "The 4th", "The 5th"),
  values = c(5, 4, 3, 2, 1))

p
```
### Set Marker Size and Color in Area Funnel Plots
```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly(
  type = "funnelarea",
  values = c(5, 4, 3, 2, 1),
  text = c("The 1st","The 2nd", "The 3rd", "The 4th", "The 5th"),
  marker = list(colors = c("deepskyblue", "lightsalmon", "tan", "teal", "silver"),
                line = list(color = c("wheat", "wheat", "blue", "wheat", "wheat"), width = c(0, 1, 5, 0, 4))),
  textfont = list(family = "Old Standard TT, serif", size = 13, color = "black"),
  opacity = 0.65)

p
```

### Multiple Area Funnels
```{r}
# Need to install plotly from Github to get funnel plots
# devtools::install_github("ropensci/plotly")
library(plotly)

p <- plot_ly(
    type = "funnelarea",
    scalegroup = "first",
    values = c(500, 450, 340, 230, 220, 110),
    textinfo = "value",
    title = list(position = "top center", text = "Sales for Sale Person A in U.S."),
    domain = list(x = c(0.01, 0.48), y =c(0, 0.5))) %>%
  add_trace(
    type = "funnelarea",
    scalegroup = "first",
    values = c(600, 500, 400, 300, 200, 100),
    textinfo = "value",
    title = list(position = "top center", text = "Sales of Sale Person B in Canada"),
    domain = list(x = c(0.01, 0.48), y = c(0.56, 1))) %>%
  add_trace(
    type = "funnelarea",
    scalegroup = "second",
    values = c(510, 480, 440, 330, 220, 100),
    textinfo = "value",
    title = list(position = "top left", text = "Sales of Sale Person A in Canada"),
    domain = list(x = c(0.56, 0.98), y = c(0, 0.5))) %>%
  add_trace(
    type = "funnelarea",
    scalegroup = "second",
    values = c(360, 250, 240, 130, 120, 60),
    textinfo = "value",
    title = list(position = "top left", text = "Sales of Sale Person B in U.S."),
    domain = list(x = c(0.56, 0.98), y = c(0.56, 1))) %>%
  layout(
    margin = list(l= 200, r= 200), shapes = list(
      list(x0 = 0, x1 = 0.5, y0 = 0, y1 = 0.5),
      list(x0 = 0, x1 = 0.5, y0 = 0.55, y1 = 1),
      list(x0 = 0.55, x1 = 1, y0 = 0, y1 = 0.5),
      list(x0 = 0.55, x1 = 1, y0 = 0.55, y1 = 1)))

p
```

```{r, echo=FALSE, message=FALSE, results="hide"}
# Remove plotly install from github
remove.packages("plotly")
# Install plotly from CRAN
install.packages("plotly", repos = "http://cran.us.r-project.org")
```

#Reference

See [https://plot.ly/r/reference/#funnel](https://plot.ly/r/reference/#funnel) and [https://plot.ly/r/reference/#funnelarea](https://plot.ly/r/reference/#funnelarea) for more information and chart attribute options!
