---
name: Waterfall Charts
permalink: r/waterfall-charts/
description: How to make waterfall charts in R with Plotly.
layout: base
thumbnail: thumbnail/waterfall-charts.jpg
language: r
page_type: example_index
display_as: financial
order: 4
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Waterfall Chart

```{r}
library(plotly)

x= list("Sales", "Consulting", "Net revenue", "Purchases", "Other expenses", "Profit before tax")
measure= c("relative", "relative", "total", "relative", "relative", "total")
text= c("+60", "+80", "", "-40", "-20", "Total")
y= c(60, 80, 0, -40, -20, 0)
data = data.frame(x=factor(x,levels=x),measure,text,y)

p <- plot_ly(
  data, name = "20", type = "waterfall", measure = ~measure,
  x = ~x, textposition = "outside", y= ~y, text =~text,
  connector = list(line = list(color= "rgb(63, 63, 63)"))) %>%
  layout(title = "Profit and loss statement 2018",
        xaxis = list(title = ""),
        yaxis = list(title = ""),
        autosize = TRUE,
        showlegend = TRUE)

p
```


### Setting Marker Size and Color
This example uses [decreasing, increasing, and total attributes](https://plot.ly/r/reference/#waterfall-decreasing-marker-line-color) to customize the bars.

```{r}
library(plotly)

y = c(375, 128, 78, 0, -327, -78, 0, 32, 89, 0, -45, 0)
x = c("Sales", "Consulting", "Maintenance", "Net revenue", "Purchases", "Material expenses", "Operating profit", "Investment income", "Financial income",
"Profit before tax", "Income tax (15%)", "Profit after tax")
measure = c("relative", "relative", "relative", "total", "relative", "relative", "total", "relative", "relative", "total", "relative", "total")
data = data.frame(x=factor(x,levels = x), y, measure)

P <- plot_ly(data, x = ~x, y = ~y, measure = ~measure, type = "waterfall", base = 300, decreasing = list(marker = list(color = "Maroon", line = list(color = "red", width = 2))),
increasing = (marker = list(color = "Teal")),
totals = list(marker = list(color = "deep sky blue", line = list(color = 'blue', width = 3))))%>%
layout(title = "Profit and loss statement", xaxis = list(title = "", tickfont = "16", ticks = "outside"),
yaxis = list(title = ""), waterfallgap = "0.3")


P
```

```{r}
library(plotly)

x = c(375, 128, 78, 27, 0, -327, -12, -78, -12, 0, 32, 89, 0, -45, 0)
y = c("Sales", "Consulting", "Maintenance", "Other revenue", "Net revenue", "Purchases", "Material expenses",
"Personnel expenses", "Other expenses", "Operating profit", "Investment income", "Financial income",
"Profit before tax", "Income tax (15%)", "Profit after tax")
measure = c("relative", "relative", "relative", "relative", "total", "relative", "relative", "relative",
"relative", "total", "relative", "relative", "total", "relative", "total")
data = data.frame(x,y=factor(y,levels = y), measure)

P <- plot_ly(data, x = ~x, y = ~y, measure = ~measure, type = "waterfall", name = "2018",
orientation = "h", connector = list(mode = "between", line = list(width = 4, color = "rgb(0, 0, 0)", dash = 0)))%>%
layout(title = "Profit and loss statement 2018<br>waterfall chart displaying positive and negative",
xaxis = list(title = "", tickfont = "16", ticks = "outside"),
yaxis = list(title = "", type = "category", autorange = "reversed"),
        xaxis = list(title ="", type = "linear"),
        margin = c(l = 150),
        showlegend = TRUE)


P
```
