---
name: Gauge Chart
permalink: r/gauge-charts/
description: How to create a Gauge Chart in R with Plotly
layout: base
thumbnail: thumbnail/gauge.jpg
language: r
redirect_from: r/gauge-meter
display_as: financial
order: 7
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Gauge

  A radial gauge chart has a circular arc, which displays a single value to estimate progress toward a goal.
  The bar shows the target value, and the shading represents the progress toward that goal. Gauge charts, known as
  speedometer charts as well. This chart type is usually used to illustrate key business indicators.

  The example below displays a basic gauge chart with default attributes. For more information about different added attributes check [indicator](https://plot.ly/r/indicator/) tutorial.

```{r}
library(plotly)

p <- plot_ly(
    domain = list(x = c(0, 1), y = c(0, 1)),
    value = 270,
    title = list(text = "Speed"),
    type = "indicator",
    mode = "gauge+number") %>%
  layout(margin = list(l=20,r=30))

p
```
### Add Steps, Threshold, and Delta

The following examples include "steps" attribute shown as shading inside the radial arc, "delta" which is the
  difference of the value and goal (reference - value), and "threshold" to determine boundaries that visually alert you if the value cross a defined threshold.

```{r}
library(plotly)

p <- plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = 450,
  title = list(text = "Speed"),
  type = "indicator",
  mode = "gauge+number+delta",
  delta = list(reference = 380),
  gauge = list(
    axis =list(range = list(NULL, 500)),
    steps = list(
      list(range = c(0, 250), color = "lightgray"),
      list(range = c(250, 400), color = "gray")),
    threshold = list(
      line = list(color = "red", width = 4),
      thickness = 0.75,
      value = 490))) %>%
  layout(margin = list(l=20,r=30))

p
```

### Custom Gauge Chart
The following example shows how to style your gauge charts. For more information about all possible options check our [reference page](https://plot.ly/r/reference/#indicator).

```{r}
library(plotly)

p <- plot_ly(
  type = "indicator",
  mode = "gauge+number+delta",
  value = 420,
  title = list(text = "Speed", font = list(size = 24)),
  delta = list(reference = 400, increasing = list(color = "RebeccaPurple")),
  gauge = list(
    axis = list(range = list(NULL, 500), tickwidth = 1, tickcolor = "darkblue"),
    bar = list(color = "darkblue"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    steps = list(
      list(range = c(0, 250), color = "cyan"),
      list(range = c(250, 400), color = "royalblue")),
    threshold = list(
      line = list(color = "red", width = 4),
      thickness = 0.75,
      value = 490))) %>%
  layout(
    margin = list(l=20,r=30),
    paper_bgcolor = "lavender",
    font = list(color = "darkblue", family = "Arial"))

p
```

#Reference

See [https://plot.ly/r/reference/#indicator](https://plot.ly/r/reference/#indicator) for more information and chart attribute options!
