---
title: Group By in R | Examples | Plotly
name: Group By
permalink: r/group-by/
description: How to use groupby transforms in R with Plotly.
layout: base
thumbnail: thumbnail/groupby.jpg
language: r
has_thumbnail: true
display_as: transforms
page_type: example_index
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

#### Basic Example

```{r, results='hide'}
library(plotly)

p <- plot_ly(
  type = 'scatter',
  x = mtcars$hp,
  y = mtcars$qsec,
  text = paste("Make: ", rownames(mtcars),
               "<br>hp: ", mtcars$hp,
               "<br>qsec: ", mtcars$qsec,
               "<br>Cyl: ", mtcars$cyl),
  hoverinfo = 'text',
  mode = 'markers',
  transforms = list(
    list(
      type = 'groupby',
      groups = mtcars$cyl,
      styles = list(
        list(target = 4, value = list(marker =list(color = 'blue'))),
        list(target = 6, value = list(marker =list(color = 'red'))),
        list(target = 8, value = list(marker =list(color = 'black')))
      )
      )
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link <- api_create(p, filename = "groupby-basic")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

#### Reference

See [https://plot.ly/r/reference/](https://plot.ly/r/reference/) for more information and options!