---
title: Range Sliders and Selectors in R | Examples | Plotly
name: Range Sliders and Selectors
permalink: r/range-slider/
description: How to use range-sliders and range-selectors in R
layout: base
thumbnail: thumbnail/sliders.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: controls
order: 2
output:
  html_document:
    keep_md: yes
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Range Slider and Selector Buttons

```{r, results = 'hide'}
library(plotly)
library(quantmod)

# Download some data
getSymbols(Symbols = c("AAPL", "MSFT"))

ds <- data.frame(Date = index(AAPL), AAPL[,6], MSFT[,6])

p <- plot_ly(ds, x = ~Date) %>%
  add_lines(y = ~AAPL.Adjusted, name = "Apple") %>%
  add_lines(y = ~MSFT.Adjusted, name = "Microsoft") %>%
  layout(
    title = "Stock Prices",
    xaxis = list(
      rangeselector = list(
        buttons = list(
          list(
            count = 3,
            label = "3 mo",
            step = "month",
            stepmode = "backward"),
          list(
            count = 6,
            label = "6 mo",
            step = "month",
            stepmode = "backward"),
          list(
            count = 1,
            label = "1 yr",
            step = "year",
            stepmode = "backward"),
          list(
            count = 1,
            label = "YTD",
            step = "year",
            stepmode = "todate"),
          list(step = "all"))),

      rangeslider = list(type = "date")),

    yaxis = list(title = "Price"))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="rangeslider")
chart_link
```

```{r, echo=FALSE}
chart_link
```
