---
title: Dot Plots in R | Examples | Plotly
name: Dot Plots
permalink: r/dot-plots/
description: How to make a dot plot in R. Dot plots show changes between two points in time or between two conditions.
layout: base
thumbnail: thumbnail/dot-plot.jpg
language: r
has_thumbnail: true
display_as: basic
order: 7.5
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

# Dot and Dumbbell Plots

```{r, results = 'hide'}
s <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")
s <- s[order(s$Men), ]

p <- plot_ly(s, x = ~Women, y = ~School, name = "Women", type = 'scatter',
             mode = "markers", marker = list(color = "pink")) %>%
  add_trace(x = ~Men, y = ~School, name = "Men",type = 'scatter',
            mode = "markers", marker = list(color = "blue")) %>%
  layout(
    title = "Gender earnings disparity",
    xaxis = list(title = "Annual Salary (in thousands)"),
    margin = list(l = 100)
  )

chart_link = api_create(p, filename="dot-basic-dot-plot")
chart_link
```

```{r, echo=FALSE}
chart_link
```

#Reference

See [https://plot.ly/r/reference/#scatter](https://plot.ly/r/reference/#scatter) for more information and chart attribute options!
