---
title: Embed Logos in Plotly Graphs with R
name: Embedding Logos in Plotly Graphs
permalink: r/logos/
description: How to embed logos and images into Plotly charts.
layout: base
thumbnail: thumbnail/get-requests.jpg
language: r
page_type: example_index
has_thumbnail: false
display_as: style_opt
order: 6
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```
### Embed Logos on a Graph

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(x = c(1, 2, 3), y = c(1, 2, 3)) %>%
  add_lines() %>%
  layout(
    images = list(
      list(source = "https://images.plot.ly/language-icons/api-home/python-logo.png",
           xref = "paper",
           yref = "paper",
           x= 0,
           y= 1,
           sizex = 0.2,
           sizey = 0.2,
           opacity = 0.8
      ),

      list(source = "https://images.plot.ly/language-icons/api-home/matlab-logo.png",
           xref = "x",
           yref = "paper",
           x = 2.7,
           y = 0.25,
           sizex = 0.4,
           sizey = 0.8,
           opacity = 0.8
      ),

      list(source =  "https://images.plot.ly/language-icons/api-home/r-logo.png",
           xref = "x",
           yref = "y",
           x = 0.9,
           y = 3.1,
           sizex = 2,
           sizey = 2,
           sizing = "stretch",
           opacity = 0.4,
           layer = "below"
      )
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="logos-1")
chart_link
```

```{r, echo=FALSE}
chart_link
```
