---
name: Colorscales
permalink: r/colorscales/
description: How to create colorscales in R with Plotly.
layout: base
language: r
page_type: example_index
display_as: style_opt
order: 6
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Colorscale for Scatter Plots

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
  type = 'scatter',
  mode='markers',
  y=rep(5, 40),
  marker=list(
    size=seq(0, 39),
    color=seq(0, 39),
    colorbar=list(
      title='Colorbar'
    ),
    colorscale='Viridis',
    reversescale =T
  )
  ) %>%
  layout(
    xaxis = list(
      showgrid = F,
      zeroline = F
    ),
    yaxis = list(
      showgrid = F,
      zeroline = F
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="colorscales-scatter")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Colorscale Contour

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
  type = 'contour',
  z=matrix(c(10, 10.625, 12.5, 15.625, 20,
      5.625, 6.25, 8.125, 11.25, 15.625,
      2.5, 3.125, 5., 8.125, 12.5,
      0.625, 1.25, 3.125, 6.25, 10.625,
      0, 0.625, 2.5, 5.625, 10),
      nrow=5, ncol=5)
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="colorscales-contour")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Share Color Axis

This example shows how to specify the color scale and color bar per trace. To share colorscale information in multiple subplots, you can use [coloraxis](https://plot.ly/r/reference/#scatter-marker-line-coloraxis).
Below we show how to set a reference coloraxis1 to a shared coloraxis, which are set in the layout. Note that multiple color scales can be linked to the same color.

```{r, results = 'hide'}
library(plotly)

plot_ly(
    type = "heatmap",
    x = c(1,2,3,4),
    z = list(c(1,2,3,4), c(4,-3,-1,1)),
    coloraxis = 'coloraxis')
p2 <- plot_ly(
    type = "heatmap",
    x = c(3,4,5,6),
    z = list(c(10,2,1,0), c(4,3,5,6)),
    coloraxis = 'coloraxis')
p <- subplot(p1, p2) %>%
  layout(coloraxis=list(colorscale='Jet'))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="coloraxis")
chart_link
```

```{r, echo=FALSE}
chart_link
```

#Reference

See [https://plot.ly/r/reference/#heatmap-colorscale](https://plot.ly/r/reference/#heatmap-colorscale) for more information and options!
