---
name: Colorway
permalink: r/colorway/
description: How to set default trace colors using colorway in R with Plotly.
layout: base
language: r
page_type: example_index
thumbnail: thumbnail/colorway.jpg
display_as: style_opt
order: 5
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Set Default Trace Colors with `colorway`

```{r}
library(plotly)

x <- seq(-1, 3, length=50)
ones <- rep(1, 50)
a_list <- seq(1, 3, length=7)
b_list <- seq(2, 14, length=7)
df <- data.frame(cbind(x, (outer((x*x), a_list) + outer(ones, b_list))))

p <- plot_ly(df, x = ~x, y = ~V2, type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~V3) %>%
  add_trace(y = ~V4) %>%
  add_trace(y = ~V5) %>%
  add_trace(y = ~V6) %>%
  add_trace(y = ~V7) %>%
  add_trace(y = ~V8) %>%
  layout(colorway = c('#f3cec9', '#e7a4b6', '#cd7eaf', '#a262a9', '#6f4d96', '#3d3b72', '#182844'))


p
```

#Reference

See [https://plot.ly/r/reference/#layout-colorway](https://plot.ly/r/reference/#layout-colorway) for more information about the colorway attribute.
