---
title: Locales | Examples | Plotly
name: Locales
permalink: r/locales/
description: How to set locales with Plotly.
layout: base
thumbnail: thumbnail/locales.jpg
language: r
has_thumbnail: true
display_as: style_opt
order: 9
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Setting Locale
To change the localization, you can use the `locale` argument in the `config()` function. 

``` {r, results = 'hide'}
library(plotly)

x <- seq.Date(Sys.Date(), Sys.Date() + 360, by = "day")

p <- plot_ly(x = x, y = rnorm(length(x))) %>%
   add_lines() %>%
  config(locale = 'zh-CN')
```

### Reference

See `?plotly::config` for more information about config options or [click here](https://plot.ly/r/configuration-options/). For more information regarding localization, [click here](https://github.com/plotly/plotly.js/tree/master/dist#to-include-localization). 
