---
description: How to make a 2D histogram in R. A 2D histogram is a visualization of
  a bivariate distribution.
display_as: statistical
language: r
layout: base
name: 2D Histograms
order: 4
output:
  html_document:
    keep_md: true
page_type: example_index
permalink: r/2D-Histogram/
thumbnail: thumbnail/histogram2d.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Basic 2D Histogram

2D histograms require `x`/`y`, but in contrast to heatmaps, `z` is optional. If `z` is not provided, binning occurs in the browser (see [here](https://plot.ly/r/reference/#histogram2d-histnorm) for a list of binning options).

```{r}
# install.packages('mvtnorm')
library(plotly)

s <- matrix(c(1, -.75, -.75, 1), ncol = 2)
obs <- mvtnorm::rmvnorm(500, sigma = s)
p <- plot_ly(x = obs[,1], y = obs[,2])
pp <- subplot(
  p %>% add_markers(alpha = 0.2),
  p %>% add_histogram2d()
)

pp
```

#### Colorscale
If `z` is not provided, the only way to control coloring is through the [colorscale attribute](https://plot.ly/r/reference/#histogram2d-colorscale)

```{r}
p <- p %>% add_histogram2d(colorscale = "Blues")

p
```

#### Z Matrix
If you want more control for the binning algorithm, you can supply a 2D table or matrix to `z`. In this case, the R package will impose it's colorscale default (and the `colors` argument can be used to control the colorscale from R):

```{r}
cnt <- with(diamonds, table(cut, clarity))
p <- plot_ly(diamonds, x = ~cut, y = ~clarity, z = ~cnt) %>%
  add_histogram2d()

p
```
