---
title: Box Plots in R | Examples | Plotly
name: Box Plots
permalink: r/box-plots/
description: How to make an interactive box plot in R. Examples of box plots in R that are grouped, colored, and display the underlying data distribution.
layout: base
thumbnail: thumbnail/box.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: statistical
order: 1
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Boxplot

```{r, results = "hide"}
library(plotly)
p <- plot_ly(y = ~rnorm(50), type = "box") %>%
  add_trace(y = ~rnorm(50, 1))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Horizontal Boxplot

```{r, results = "hide"}
library(plotly)
p <- plot_ly(x = ~rnorm(50), type = "box") %>%
  add_trace(x = ~rnorm(50, 1))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-horizontal")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Adding Jittered Points

```{r, results = "hide"}
p <- plot_ly(y = ~rnorm(50), type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-jitter")
chart_link
```

```{r, echo=FALSE}
chart_link
```


### Several Box Plots

```{r, results = "hide"}
p <- plot_ly(ggplot2::diamonds, y = ~price, color = ~cut, type = "box")

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-multiple")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Grouped Box Plots

```{r, results = "hide"}
p <- plot_ly(ggplot2::diamonds, x = ~cut, y = ~price, color = ~clarity, type = "box") %>%
  layout(boxmode = "group")

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-group")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Styling Outliers

```{r, results = "hide"}
library(plotly)

y1 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
       8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y2 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y3 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y4 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)

p <- plot_ly(type = 'box') %>%
  add_boxplot(y = y1, jitter = 0.3, pointpos = -1.8, boxpoints = 'all',
              marker = list(color = 'rgb(7,40,89)'),
              line = list(color = 'rgb(7,40,89)'),
              name = "All Points") %>%
  add_boxplot(y = y2, name = "Only Whiskers", boxpoints = FALSE,
              marker = list(color = 'rgb(9,56,125)'),
              line = list(color = 'rgb(9,56,125)')) %>%
  add_boxplot(y = y3, name = "Suspected Outlier", boxpoints = 'suspectedoutliers',
              marker = list(color = 'rgb(8,81,156)',
                            outliercolor = 'rgba(219, 64, 82, 0.6)',
                            line = list(outliercolor = 'rgba(219, 64, 82, 1.0)',
                                        outlierwidth = 2)),
              line = list(color = 'rgb(8,81,156)')) %>%
  add_boxplot(y = y4, name = "Whiskers and Outliers", boxpoints = 'outliers',
              marker = list(color = 'rgb(107,174,214)'),
              line = list(color = 'rgb(107,174,214)')) %>%
  layout(title = "Box Plot Styling Outliers")

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="box-styled")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Reference

See [https://plot.ly/r/reference/#box](https://plot.ly/r/reference/#box) for more information and chart attribute options!
