---
title: ggplot2 scale_y_continuous | Examples | Plotly
name: scale_y_continuous
permalink: ggplot2/scale-y/
description: How to use logarithmic scales with ggplot2 axes.
layout: base
thumbnail: thumbnail/log.jpg
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

## Basic

```{r, results='hide'}
library(plotly)

p <- ggplot(diamonds, aes(color, log10(price))) +
    geom_boxplot() +
    scale_y_continuous("Price, log10-scaling")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="scaley/basic")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a href="http://stackoverflow.com/questions/4699493/transform-only-one-axis-to-log10-scale-with-ggplot2">Stack Overflow</a>.