---
title: ggplot2 scale_x_date | Examples | Plotly
name: scale_x_date
permalink: ggplot2/scale-x/
description: How to make plots in R and ggplot2 using scale_x_date.
layout: base
thumbnail: thumbnail/time-series.jpg
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="bdun9")
Sys.setenv("plotly_api_key"="ukqr128tmk")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

## By Month

```{r, results='hide'}
library(plotly)

x <- c("04-01-10","05-01-10","06-01-10","07-01-10","08-01-10","09-01-10","10-01-10","11-01-10","12-01-10","01-01-11","02-01-11","03-01-11","04-01-11","05-01-11","06-01-11","07-01-11","08-01-11","09-01-11","10-01-11","11-01-11","12-01-11","01-01-12","02-01-12","03-01-12","04-01-12","05-01-12","06-01-12")
y <- c(120,210,130,160,190,210,80,70,110,120,140,160,130,200,110,180,210,200,90,60,100,100,120,170,100,180,120)

MySample <- data.frame(x) ## convert to dataframe
MySample$y <- y

# install.packages("lubridate")
require(lubridate)

MySample$date <- as.Date(MySample$x, "%m-%d-%y")
MySample$year <- year(MySample$date)

p <- ggplot(MySample, aes(date, y, fill = year)) +
    geom_bar(y=y,stat="identity") +
    facet_grid(. ~ year, scales = "free") +
    scale_x_date(labels = date_format("%b/%y")) +
    scale_fill_gradient(breaks=unique(MySample$year))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="scalex/month")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a href="http://stackoverflow.com/questions/11472856/month-year-bar-graph-plot-faceted-and-filled-on-year-with-data-input-as-date-in?rq=1">Stack Overflow</a>.

## By Year

```{r, results='hide'}
library(plotly)

set.seed(12345)
Date <- seq(as.Date("2010/1/1"), as.Date("2014/1/1"), "week")
Y <- rnorm(n=length(Date), mean=100, sd=1)
df <- data.frame(Date, Y)

df$Year <- format(df$Date, "%Y")
df$Month <- format(df$Date, "%b")
df$Day <- format(df$Date, "%d")

df$MonthDay <- format(df$Date, "%d-%b")

df$CommonDate <- as.Date(paste0("2000-",format(df$Date, "%j")), "%Y-%j")

p <- ggplot(data = df,
     mapping = aes(x = CommonDate, y = Y, shape = Year, colour = Year)) +
     geom_point() +
     geom_line() +
     facet_grid(facets = Year ~ .) +
     scale_x_date(labels = function(x) format(x, "%d-%b"))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="scalex/year")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a href="http://stackoverflow.com/questions/11472856/month-year-bar-graph-plot-faceted-and-filled-on-year-with-data-input-as-date-in?rq=1">Stack Overflow</a>.


