---
title: geom_errorbar | Examples | Plotly
name: geom_errorbar
permalink: ggplot2/geom_errorbar/
description: Examples of geom_errobar in R and ggplot2
layout: base
thumbnail: thumbnail/error-bar.jpg
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: statistics
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Basic Error Bar

```{r, results='hide'}
library(plotly)

df <- data.frame(x = 1:10,
                 y = 1:10,
                 ymin = (1:10) - runif(10),
                 ymax = (1:10) + runif(10),
                 xmin = (1:10) - runif(10),
                 xmax = (1:10) + runif(10))

p <- ggplot(data = df,aes(x = x,y = y)) + 
    geom_point() + 
    geom_errorbar(aes(ymin = ymin,ymax = ymax)) + 
    geom_errorbarh(aes(xmin = xmin,xmax = xmax))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_errorbar/basic")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Margin Error Bar

```{r, results='hide'}
library(plotly)

population <- data.frame(Year=seq(1790, 1970, length.out=length(uspop)), 
                         Population=uspop, 
                         Error=rnorm(length(uspop), 5))

library(ggplot2)
p <- ggplot(population, aes(x=Year, y=Population, 
                       ymin=Population-Error, ymax=Population+Error))+
  geom_line()+
  geom_point(pch=2)+
  geom_errorbar(width=0.9)

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_errorbar/margin")
chart_link
```

``` {r, echo=FALSE}
chart_link
```