---
name: interactive tooltip
permalink: ggplot2/interactive-tooltip/
description: How to add custom tooltip effects to R and ggplot2 charts with JavaScript.
layout: base
thumbnail: thumbnail/hover.jpg
language: ggplot2
page_type: example_index
display_as: layout_opt
redirect_from: ggplot2/maps/
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Maps

```{r}
library(plotly)

data(canada.cities, package="maps")
p <- ggplot(canada.cities, aes(long, lat)) +
        borders(regions="canada", name="borders") +
        coord_equal() +
        geom_point(aes(text=name, size=pop), colour="red", alpha=1/2, name="cities")

p <- ggplotly(p)

p
```


### Custom Tooltip

```{r}
library(plotly)
#install.packages("gapminder")
library(gapminder)

p <- ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent, text =      paste("country:", country))) +
     geom_point(alpha = (1/3)) + scale_x_log10()  
  
p <- ggplotly(p)

p
```
Inspired by <a href="https://github.com/jennybc/ggplot2-tutorial/blob/master/gapminder-ggplot2-scatterplot.md">Gapminder Tutorial</a>

### Control Events

```{r}
library(plotly)
#install.packages("gapminder")
library(gapminder)

p <- ggplot(gapminder, aes(x = year, y = lifeExp, text = paste("country:",country))) + 
     geom_point() +
     facet_wrap(~ continent) 

p <- ggplotly(p)

p
```
Inspired by <a href="https://github.com/jennybc/ggplot2-tutorial/blob/master/gapminder-ggplot2-scatterplot.md">Gapminder Tutorial</a>
