---
title: geom_point | Examples | Plotly
name: geom_point
permalink: ggplot2/geom_point/
description: How to make a scatter chart in ggplot2. Examples of scatter charts and line charts with fits and regressions.
layout: base
thumbnail: thumbnail/gg-themes.jpg
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: basic
order: 6
redirect_from: ggplot2/line-and-scatter/
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Scatter Chart

```{r, results='hide'}
library(plotly)

set.seed(955)
# Make some noisily increasing data
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

p <- ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1)      # Use hollow circles

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/scatter")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Liner Regression w/ smooth

```{r, results='hide'}
library(plotly)

set.seed(955)
# Make some noisily increasing data
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

p <- ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm)   # Add linear regression line


p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/linear-reg")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Without Shading

```{r, results='hide'}
library(plotly)

set.seed(955)
# Make some noisily increasing data
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

p <- ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/no-shading")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Loess Smoothed Fit

```{r, results='hide'}
library(plotly)

set.seed(955)
# Make some noisily increasing data
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

p <- ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth()            # Add a loess smoothed fit curve with confidence region
# > geom_smooth: method="auto" and size of largest group is less than 1000, so using loess.
# Use 'method = x' to change the smoothing method.

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/loess")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Constrained Slope

```{r, results='hide'}
library(plotly)

set.seed(1234)

n <- 20

x1 <- rnorm(n); x2 <- rnorm(n)
y1 <- 2 * x1 + rnorm(n)
y2 <- 3 * x2 + (2 + rnorm(n))
A <- as.factor(rep(c(1, 2), each = n))
df <- data.frame(x = c(x1, x2), y = c(y1, y2), A = A)
fm <- lm(y ~ x + A, data = df)

p <- ggplot(data = cbind(df, pred = predict(fm)), aes(x = x, y = y, color = A))
p <- p + geom_point() + geom_line(aes(y = pred))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/slope")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspire by <a #href="http://stackoverflow.com/questions/4251294/constraining-slope-in-stat-smooth-with-ggplot-plotting-ancova">Stack Overflow</a>

### Stat Summary

```{r, results='hide'}
library(plotly)

hist <- data.frame(date=Sys.Date() + 0:13, counts=1:14)
hist <- transform(hist, weekday=factor(weekdays(date), levels=c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday')))

p <- ggplot(hist, aes(x=weekday, y=counts, group=1)) +
    geom_point(stat='summary', fun.y=sum) +
    stat_summary(fun.y=sum, geom="line")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/stat-summary")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspire by <a #href="http://stackoverflow.com/questions/16350720/using-geom-line-with-x-axis-being-factors">Stack Overflow</a> 

### Control Line Order

```{r, results='hide'}
library(plotly)

dat <- data.frame(x = sample(1:10), y = sample(1:10), order = sample(1:10))
p <- ggplot(dat[order(dat$order),], aes(x, y)) + geom_point() + geom_text(aes(y = y + 0.25,label =      order)) +
     geom_path()

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/control-line")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Horizontal Line w/ Segment

```{r, results='hide'}
library(plotly)

p <- ggplot(mtcars,aes(mpg,qsec))+geom_point() +
  geom_segment(aes(x=15,xend=20,y=18,yend=18))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/horizontal-line")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a #href="http://stackoverflow.com/questions/20311718/add-horizontal-line-to-ggplot-for-specified-interval-of-x-axis">Stack Overflow</a>

### Add Points

```{r, results='hide'}
library(plotly)

df <- data.frame(time=as.factor(c(1,1,2,2,3,3,4,4,5,5)), 
               value=as.numeric(c(7, 8, 9, 10, 10, 11, 10.5, 11.4, 10.9, 11.6)), 
               side=as.factor(c("E","F","E","F","E","F","E","F","E","F")))


p <- ggplot(df, aes(time, value, group=side, colour=side)) + 
     geom_line(size=1)
p <- p + geom_point()

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/add-points")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Add Regression w/ Abline

```{r, results='hide'}
library(plotly)

set.seed(1)
x <-  1:10
dd <- rbind(data.frame(x=x,fac="a", y=x+rnorm(10)),
            data.frame(x=2*x,fac="b", y=x+rnorm(10)))
coef <- lm(y~x:fac, data=dd)$coefficients
p <- qplot(data=dd, x=x, y=y, color=fac)+
    geom_abline(slope=coef["x:faca"], intercept=coef["(Intercept)"])+
    geom_abline(slope=coef["x:facb"], intercept=coef["(Intercept)"])

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_point/regression")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a #href="http://stats.stackexchange.com/questions/39233/regression-lines-with-same-intercept">Stats Exchange</a>