---
title: ggplot2 axis.title | Examples | Plotly
name: axis.title
permalink: ggplot2/axis-title/
description: How to modify axis titles in R and ggplot2.
layout: base
thumbnail: thumbnail/theme_image.png
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Axis Labels

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

# To set x-axis and y-axis labels use labs()
p <- ggplot(df, aes(carat, price)) + 
  geom_point() + 
  labs(title = "Diamonds", x = "x-axis -> Carat", y = "y-axis -> Price")

p <- ggplotly(p)

# Alternatively use
p <- ggplot(df, aes(carat, price)) + 
  geom_point() + 
  ggtitle("Diamonds") + 
  xlab("x-axis -> Carat") + 
  ylab("y-axis -> Price")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-title/labels")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Axis Title Size

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(carat, price)) +
  geom_point() + 
  labs(title = "Diamonds", x = "x-axis -> Carat", y = "y-axis -> Price") +
  theme(plot.title = element_text(size = 50),  
        axis.title.x = element_text(size = 20),  
        axis.title.y = element_text(size = 20))  

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-title/size")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Axis Title Colors

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(carat, price)) +
  geom_point() + 
  labs(title = "Diamonds", x = "x-axis -> Carat", y = "y-axis -> Price") +
  theme(plot.title = element_text(size = 50, colour = "#668cff"),  
        axis.title.x = element_text(size = 20, colour = "#6699ff"),  
        axis.title.y = element_text(size = 20, colour = "#ff8080"))  

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-title/colors")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a href="http://docs.ggplot2.org/current/">ggplot2 documentation</a>
