---
title: ggplot2 Axis Text | Examples | Plotly
name: Axis Text
permalink: ggplot2/axis-text/
description: How to modify axis titles in R and ggplot2.
layout: base
thumbnail: thumbnail/theme_image.png
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: layout_opt
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Axis Text Size

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(carat, price, color = color, alpha = cut)) + 
  geom_point() + 
  theme(axis.text.x = element_text(colour = "#ff6666", size = 20), 
        axis.text.y = element_text(colour = "#668cff", size = 20))
  
p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-text/size")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Axis Text Blank

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(carat, price, color = cut)) + 
  geom_point() + 
  theme(axis.text = element_blank())

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-text/blank")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Vertical Text

```{r, results='hide'}
library(plotly)

lab <- paste("Vertical Label", c(1, 2, 3, 4, 5))

ds <- data.frame(x = sample(lab, size = 1000, replace = T),
                 y = sample(LETTERS[1:5], size = 1000, replace = T))

p <- ggplot(ds, aes(x = x, fill = y)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  ggtitle("Vertical Axis Labels")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-text/vertical")
chart_link
```

``` {r, echo=FALSE}
chart_link
```

### Angled Text

```{r, results='hide'}
library(plotly)

lab <- paste("Angle Label", c(1, 2, 3, 4, 5))

ds <- data.frame(x = sample(lab, size = 1000, replace = T),
                 y = sample(LETTERS[1:5], size = 1000, replace = T))

p <- ggplot(ds, aes(x = x, fill = y)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 45)) + 
  ggtitle("Angle Axis Labels")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="axis-text/angled")
chart_link
```

``` {r, echo=FALSE}
chart_link
```
Inspired by <a href="http://docs.ggplot2.org/current/">ggplot2 documentation</a>
