---
title: geom_bar| Examples | Plotly
name: geom_bar
permalink: ggplot2/geom_bar/
description: How to make a bar chart in ggplot2 using geom_bar. Examples of grouped, stacked, overlaid, filled, and colored bar charts.
layout: base
thumbnail: thumbnail/bar.jpg
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: basic
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Bar Chart

```{r, results='hide'}
library(plotly)

dat <- data.frame(
    time = factor(c("Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(14.89, 17.23)
)

p <- ggplot(data=dat, aes(x=time, y=total_bill)) +
    geom_bar(stat="identity")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-chart")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Colored Bar Chart
filled bar chart with <code>geom_bar</code>

```{r, results='hide'}
library(plotly)

dat <- data.frame(
    time = factor(c("Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(14.89, 17.23)
)

p <- ggplot(data=dat, aes(x=time, y=total_bill, fill=time)) +
    geom_bar(stat="identity")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-colored")
chart_link
```

```{r echo=FALSE}
chart_link
```

### No Legend
<code>geom_bar</code> with no legend

```{r, results='hide'}
library(plotly)

dat <- data.frame(
    time = factor(c("Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(14.89, 17.23)
)

# No legend, since the information is redundant
p <- ggplot(data=dat, aes(x=time, y=total_bill, fill=time)) +
    geom_bar(colour="black", stat="identity") +
    guides(fill=FALSE)

p <- ggplotly(p)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-no-legend")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Position Dodge
<code>geom_bar</code> with <code>position_dodge</code>

```{r, results='hide'}
library(plotly)

dat1 <- data.frame(
    sex = factor(c("Female","Female","Male","Male")),
    time = factor(c("Lunch","Dinner","Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(13.53, 16.81, 16.24, 17.42)
)

# Bar graph, time on x-axis, color fill grouped by sex -- use position_dodge()
p <- ggplot(data=dat1, aes(x=time, y=total_bill, fill=sex)) +
    geom_bar(stat="identity", position=position_dodge())

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-position-dodge")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Custom Colors
<code>geom_bar</code> with manual colors

```{r, results='hide'}
library(plotly)

dat1 <- data.frame(
    sex = factor(c("Female","Female","Male","Male")),
    time = factor(c("Lunch","Dinner","Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(13.53, 16.81, 16.24, 17.42)
)

p <- ggplot(data=dat1, aes(x=time, y=total_bill, fill=sex)) +
    geom_bar(stat="identity", position=position_dodge(), colour="black") +
    scale_fill_manual(values=c("#999999", "#E69F00"))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-custom-colors")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Styles & Themes
<code>geom_bar</code> with styles and theme

```{r, results='hide'}
library(plotly)

dat1 <- data.frame(
    sex = factor(c("Female","Female","Male","Male")),
    time = factor(c("Lunch","Dinner","Lunch","Dinner"), levels=c("Lunch","Dinner")),
    total_bill = c(13.53, 16.81, 16.24, 17.42)
)

# A bar graph
p <- ggplot(data=dat1, aes(x=time, y=total_bill, fill=sex)) +
    geom_bar(colour="black", stat="identity",
             position=position_dodge(),
             size=.3) +                        # Thinner lines
    xlab("Time of day") + ylab("Total bill") + # Set axis labels
    ggtitle("Average bill for 2 people") +     # Set title
    theme_bw()

p <- ggplotly(p)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-themes")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Variable Comparison
using <code>geom_bar</code> for variable comparison

```{r, results='hide'}
library(plotly)

DF <- read.table(text="Rank F1     F2     F3
1    500    250    50
2    400    100    30
3    300    155    100
4    200    90     10", header=TRUE)

library(reshape2)
DF1 <- melt(DF, id.var="Rank")

p <- ggplot(DF1, aes(x = Rank, y = value, fill = variable)) +
  geom_bar(stat = "identity")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-comparison")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Error Bars
barplot with error bars

```{r, results='hide'}
library(plotly)
library(dplyr)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

df.summ <- df %>% group_by(cut) %>% summarize(Mean = mean(table), Min = min(table), Max = max(table))

p <- ggplot(df.summ, aes(x = cut, y = Mean, ymin = Min, ymax = Max, fill = cut)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar() + 
  ggtitle("Bar chart with Error Bars")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-error")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Stacked Bar Chart
<code>geom_bar</code> with stacked traces

```{r, results='hide'}
library(plotly)
library(dplyr)

df <- structure(c(106487, 495681, 1597442, 2452577, 2065141, 2271925, 4735484, 3555352, 8056040, 4321887, 2463194, 347566, 621147, 1325727, 1123492, 800368, 761550, 1359737, 1073726, 36, 53, 141, 41538, 64759, 124160, 69942, 74862, 323543, 247236, 112059, 16595, 37028, 153249, 427642, 1588178, 2738157, 2795672, 2265696, 11951, 33424, 62469, 74720, 166607, 404044, 426967, 38972, 361888, 1143671, 1516716, 160037, 354804, 996944, 1716374, 1982735, 3615225, 4486806, 3037122, 17, 54, 55, 210, 312, 358, 857, 350, 7368, 8443, 6286, 1750, 7367, 14092, 28954, 80779, 176893, 354939, 446792, 33333, 69911, 53144, 29169, 18005, 11704, 13363, 18028, 46547, 14574, 8954, 2483, 14693, 25467, 25215, 41254, 46237, 98263, 185986), .Dim = c(19, 5), .Dimnames = list(c("1820-30", "1831-40", "1841-50", "1851-60", "1861-70", "1871-80", "1881-90", "1891-00", "1901-10", "1911-20", "1921-30", "1931-40", "1941-50", "1951-60", "1961-70", "1971-80", "1981-90", "1991-00", "2001-06"), c("Europe", "Asia", "Americas", "Africa", "Oceania")))
df.m <- melt(df)
df.m <- rename(df.m, Period = Var1, Region = Var2)

p <- ggplot(df.m, aes(x = Period, y = value/1e+06,fill = Region)) + ggtitle("Migration to the United States by Source Region (1820-2006), In Millions")
p <- p + geom_bar(stat = "identity", position = "stack")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-stacked")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Ordered Bar Chart
ordering variable in <code>geom_bar</code>

```{r, results='hide'}
library(plotly)
library(plyr)

dane<-data.frame(x=1:10,y=seq(-5,4),g=rep(c('A','B'),each=5))
dane$x<-as.factor(dane$x)

p <- ggplot(data=dane,aes(x=x,y=y,fill=g)) +
    geom_bar(stat="identity")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-ordered")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Precentages
using <code>geom_bar</code> to show percentages

```{r, results='hide'}
library(plotly)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(x = color)) + 
  geom_bar(aes(y = ..count../sum(..count..), fill = cut)) + 
  scale_fill_brewer(palette = "Set3") + 
  ylab("Percent") + 
  ggtitle("Show precentages in bar chart")
  
p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-percentages")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Manuel Colors
using <code>geom_bar</code> to manually specify colors

```{r, results='hide'}
library(plotly)
library(RColorBrewer)
set.seed(123)

df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

# Simply use fill = a vector of colors
p <- ggplot(df, aes(x = color)) +
  geom_bar(fill = brewer.pal(length(unique(df$color)), "Set3")) + 
  ylab("Count") + 
  ggtitle("Specify manual colors in a bar chart")
  
p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-manuel")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Reordered Bar Chart
Re-ordering bars shown using <code>geom_bar</code>

```{r, results='hide'}
library(plotly)

df <- data.frame(x = as.factor(LETTERS[1:5]), 
                 y = sample(10:20, size = 5))

# First change factor levels
df$x <- factor(df$x, levels = c("C", "B", "A", "D", "E"))

# Plot
p <- ggplot(df, aes(x, y, fill = x)) + 
  geom_bar(stat = "identity") +
  ggtitle("Bar Chart with changed factor levels")

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bar/bar-reordered")
chart_link
```

```{r echo=FALSE}
chart_link
```