---
title: Intro to Animations | Examples | Plotly
name: Intro to Animations
permalink: ggplot2/animations/
description: How to create animations in ggplot2 with Plotly.
layout: base
thumbnail: thumbnail/animations.gif
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: animations
order: 1
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Frames

Now, along with `data` and `layout`, `frames` is added to the keys that `figure` allows. Your `frames` key points to a list of figures, each of which will be cycled through upon instantiation of the plot.

### Basic Example

```{r, results = 'hide'}
library(plotly)

df <- data.frame(
  x = c(1,2,3,4), 
  y = c(1,2,3,4), 
  f = c(1,2,3,4)
)

p <- ggplot(df, aes(x, y)) +
    geom_point(aes(frame = f))

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Mulitple Trace Animations

```{r, results = 'hide'}
library(plotly)
library(gapminder)


p <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
  geom_point(aes(size = pop, frame = year, ids = country)) +
  scale_x_log10()

p <- ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/mulitple-trace")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Add Animation Options

```{r, results = 'hide'}
library(plotly)

p <- p %>% 
  animation_opts(
    1000, easing = "elastic", redraw = FALSE
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/animation-options")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Add Button Options

```{r, results = 'hide'}
library(plotly)

p <- p %>% 
  animation_button(
    x = 1, xanchor = "right", y = 0, yanchor = "bottom"
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/button-options")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Add Slider Options

```{r, results = 'hide'}
library(plotly)

p <- p %>%
  animation_slider(
    currentvalue = list(prefix = "YEAR ", font = list(color="red"))
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/slider-options")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Advanced Example

```{r, results = 'hide'}
library(plotly)
library(gapminder)

p <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
  geom_point(aes(size = pop, frame = year, ids = country)) +
  scale_x_log10()

p <- ggplotly(p) %>% 
  animation_opts(
    1000, easing = "elastic", redraw = FALSE
  ) %>% 
  animation_button(
    x = 1, xanchor = "right", y = 0, yanchor = "bottom"
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "YEAR ", font = list(color="red"))
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="gganimations/advanced")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Reference 

To read more on animations see [The Plotly Book](https://cpsievert.github.io/plotly_book/key-frame-animations.html).
