---
title: Cumulative Animations | Examples | Plotly
name: Cumulative Animations
permalink: ggplot2/cumulative-animations/
description: How to create cumulative animations in ggplot2 with Plotly.
layout: base
thumbnail: thumbnail/apple_stock_animation.gif
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: animations
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Frames

Now, along with `data` and `layout`, `frames` is added to the keys that `figure` allows. Your `frames` key points to a list of figures, each of which will be cycled through upon instantiation of the plot.

### Cumulative Lines Animation

```{r, results = 'hide'}
library(plotly)
library(quantmod)

getSymbols("AAPL",src='yahoo')

df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 30)
df$ID <- seq.int(nrow(df))

accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}

df <- df %>%
  accumulate_by(~ID)

p <- ggplot(df,aes(ID, AAPL.Close, frame = frame)) +
  geom_line()
  
p <- ggplotly(p) %>%
  layout(
    title = "AAPL: Last 30 days",
    yaxis = list(
      title = "Close",
      zeroline = F,
      tickprefix = "$"
    ),
    xaxis = list(
      title = "Day",
      zeroline = F, 
      showgrid = F
    )
  ) %>% 
  animation_opts(
    frame = 100, 
    transition = 0, 
    redraw = FALSE
  ) %>%
  animation_slider(
    currentvalue = list(
      prefix = "Day "
    )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="ggCumAnimations/lines")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Reference 

To read more on animations see [The Plotly Book](https://cpsievert.github.io/plotly_book/key-frame-animations.html).
