---
name: geom_sf
permalink: ggplot2/maps-sf/
description: How to use geom_sf with Plotly.
layout: base
thumbnail: thumbnail/sf.jpg
language: ggplot2
page_type: example_index
display_as: basic
order: 9
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Introduction

In order to complete the examples below, you'll require installing additional packages (`install.packages("packageName")`):
- [sf](https://github.com/r-spatial/sf)

The examples below use the library [simple features](https://r-spatial.github.io/sf/) to read in the shape files before plotting the features with Plotly.

### Basic sf 

``` {r}
library(plotly)
library(sf)

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)

p <- ggplotly(
  ggplot(nc) +
  geom_sf(aes(fill = AREA))
) 

p
```


### Using Native Plotly

Alternatively, you can use [`plot_ly`, `plot_geo`, or `plot_mapbox`](https://plot.ly/r/maps-sf/).

### Reference

See [https://plot.ly/r/reference/](https://plot.ly/r/reference/) for more information and chart attribute options! If you would like to read more on visualizing geo-spatial data with sf and ggplotly click [here](https://blog.cpsievert.me/2018/01/30/learning-improving-ggplotly-geom-sf/).
