---
name: geom_contour
permalink: ggplot2/geom_contour/
description: How to make a contour in ggplot2 using geom_contour.
layout: base
thumbnail: thumbnail/geom_contour.jpg
language: ggplot2
page_type: example_index
display_as: basic
order: 3
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Basic geom\_contour plot
geom\_contour produces a similar output to geom\_density\_2d, except it uses a third variable for the values rather than frequency. The volcano dataset comes pre-loaded on R.

```{r}
library(plotly)
library(reshape2)
df <- melt(volcano)

p <- ggplot(df, aes(Var1, Var2, z= value)) +
  geom_contour() +
  scale_fill_distiller(palette = "Spectral", direction = -1)
p <- ggplotly(p)

p
```

### Coloured Plot
[See here](https://ggplot2.tidyverse.org/reference/scale_brewer.html) for a list of colour palettes that come with the brewer (discrete) and distiller (continuous) packages.

```{r}
library(plotly)
library(reshape2)
df <- melt(volcano)

p <- ggplot(df, aes(Var1, Var2, z= value, colour=stat(level))) +
  geom_contour() +
  scale_colour_distiller(palette = "YlGn", direction = 1)

ggplotly(p)
```

### Filled Plot
It's possible to colour in each of the layers, by changing geom\_contour to stat\_contour as below. As the edges of the graph indicate, filled contour plots only work when each layer is an enclosed shape rather than an open line; a geom more suited to this functionality would be geom\_tile or geom\_raster.

```{r}
library(plotly)
library(reshape2)
df <- melt(volcano)

p <- ggplot(df, aes(Var1, Var2, z= value)) +
  stat_contour(geom="polygon",aes(fill=stat(level))) +
  scale_fill_distiller(palette = "Spectral", direction = -1)

ggplotly(p)
```

