---
title: geom_bin2d | Examples | Plotly
name: geom_bin2d
permalink: ggplot2/geom_bin2d/
description: How to make a bar chart in ggplot2 using geom_bin2d. Examples of filled and facetted bar charts. [UPDATE]
layout: base
thumbnail: thumbnail/bar.jpg [ADD]
language: ggplot2
page_type: example_index
has_thumbnail: true
display_as: basic
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Basic 2d Heatmap

```{r}
library(plotly)

english_french <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/english_french.csv",stringsAsFactors = FALSE)

p <- ggplot(english_french, aes(x=engperc,y=frenperc)) + 
  geom_bin2d() +
  labs(title = "Distribution of Canadian towns by English and French fluency",
       x = "% fluent in English",
       y = "% fluent in French",
       fill = "# of census \nsubdivisions")
ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bin2d/2d-chart")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Customized Colours
The automatic colour scheme is unintuitive: lighter colours denote larger numbers than darker colours.
We should change that, and while we're at it, make the colour scale logarithmic.

```{r}
library(plotly)

p <- ggplot(english_french, aes(x=engperc,y=frenperc)) + 
  geom_bin2d() +
  scale_fill_gradient(low="lightblue1",high="darkblue",trans="log10") +
  labs(title = "Distribution of Canadian towns by English and French fluency",
       x = "% fluent in English",
       y = "% fluent in French",
       fill = "# of census \nsubdivisions")
ggplotly(p)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bin2d/coloured-chart")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Weighted Data
In the previous graphs, each observation represented a single census subdivision - this counted small towns of 500 people equally with cities like Montreal and Toronto. We can weight the data by the "total" column (i.e. total population) to make this a graph of population.

```{r}
library(plotly)

p <- ggplot(english_french, aes(x=engperc, y=frenperc, weight=total)) + 
  geom_bin2d() +
  geom_bin2d(data = transform(english_french,region = "All"),bins = 20) +
  scale_fill_gradient(low="lightblue1",high="darkblue",trans="log10") +
  labs(title = "Distribution of the Canadian population by English and French fluency",
       x = "% fluent in English",
       y = "% fluent in French",
       fill = "# of people")
ggplotly(p)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bin2d/weighted-data")
chart_link
```

```{r echo=FALSE}
chart_link
```

### With Facets
We can facet the graphic with the "region" column. We can also use a little trick to add an "All" subset containing all the data.

```{r}
#{r, results='hide'}
library(plotly)

p <- ggplot(english_french, aes(x=engperc,y=frenperc, weight=total)) + 
  geom_bin2d(bins = 20) +
  geom_bin2d(data = transform(english_french,region = "All"),bins = 20) +
  facet_wrap(~factor(region, levels = c("All","Atlantic","Québec","Ontario","Prairies","British Columbia"))) +
  scale_fill_gradient(low="lightblue1",high="darkblue",trans="log10") +
  labs(title = "Distribution of Canadian towns by English and French fluency",
       x = "% fluent in English",
       y = "% fluent in French",
       fill = "# of census \nsubdivisions")
ggplotly(p)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bin2d/with-facet")
chart_link
```

```{r echo=FALSE}
chart_link
```

### Customized Appearance
We can modify the graph's appearance - for example, if the grey background makes it difficult to make out the paler shades of blue, we can change the theme to one with a white background. Included also is a way to change the font.

```{r}
library(plotly)

p <- ggplot(english_french, aes(x=engperc,y=frenperc, weight=total)) + 
  geom_bin2d(bins = 20) +
  geom_bin2d(data = transform(english_french,region = "All"),bins = 20) +
  facet_wrap(~factor(region, levels = c("All","Atlantic","Québec","Ontario","Prairies","British Columbia"))) +
  scale_fill_gradient(low="lightblue1",high="darkblue",trans="log10") +
  labs(title = "Distribution of Canadian towns by English and French fluency",
       x = "% fluent in English",
       y = "% fluent in French",
       fill = "# of census \nsubdivisions") +
  theme_bw() +
  theme(text = element_text(family = 'Fira Sans'))
ggplotly(p)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = plotly_POST(p, filename="geom_bin2d/with-facet")
chart_link
```

```{r echo=FALSE}
chart_link
```

