---
name: geom_rect
permalink: ggplot2/geom_rect/
description: How to make a timeline using geom_rect.
layout: base
thumbnail: thumbnail/geom_rect.jpg
language: ggplot2
page_type: example_index
display_as: basic
order: 8
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### geom\_rect with a line graph
geom\_rect is defined by its four sides (xmin, xmax, ymin, ymax), which are all included in the dataset. Fill refers to the colour of the rectangle, colour refers to the border, and size refers to the border width.

This line graph shows the unemployment number in the United States every month, beginning in July 1967. (This dataset comes with R.) We use geom\_rect to shade the background according to the President's party. An important note: the President does not control economic policy, something that this graph hopefully makes apparent. This is for illutrustive purposes, using a simple case and a default dataset.

```{r}
library(plotly)

library(dplyr)

df <- data.frame(name = c("Nixon", "Ford", "Carter", "Reagan", "Bush", "Clinton", "Bush", "Obama"),
                   start = as.Date(c("1969-01-20", "1974-08-09", "1977-01-20", "1981-01-20",
                             "1989-01-20", "1993-01-20", "2001-01-20", "2009-01-20")),
                   end = as.Date(c("1974-08-09", "1977-01-20", "1981-01-20", "1989-01-20", 
                           "1993-01-20", "2001-01-20", "2009-01-20", "2017-01-20")),
                   party = c("R", "R", "D", "R", "R", "D", "R", "D"),
                   stringsAsFactors = FALSE) %>%
  mutate(median_x = start + floor((end-start)/2))

p <- ggplot(economics, aes(x=date,y=unemploy)) +
  geom_rect(data=df, aes(NULL,NULL,xmin=start,xmax=end,fill=party),
            ymin=0,ymax=16000, colour="white", size=0.5, alpha=0.2) +
  scale_fill_manual(values=c("R" = "red", "D" = "blue")) +
  geom_line() +
  geom_text(data=df,aes(x=median_x,y=3000,label=name), size=3) +
  labs(title = "Unemmployment numbers since 1967",
       y = "No. unemployed (x 1000)")
p <- ggplotly(p)

p
```

### A Timeline Using geom\_rect
geom\_rect could also be the "main course" rather than just the background, for example by making a timeline.
Here are the leaders of the current European Union member countries, since 2000. Data comes from ParlGov
(which is where the parties' left-right scores come from, so please direct your complaints elsewhere). The
`LaCroixColoR` package is used and can be installed using the [instructions in the GitHub Readme](https://github.com/johannesbjork/LaCroixColoR#install-package).

```{r}
library(plotly)
library(LaCroixColoR)
library(dplyr)

european_leaders <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/european_leaders.csv",
                             stringsAsFactors = FALSE) %>%
  mutate(stint_start = as.Date(stint_start),
         stint_end = as.Date(stint_end),
         median_x = as.Date(median_x),
         left_right = as.character(left_right))

p <- ggplot(european_leaders, aes(xmin=stint_start, xmax=stint_end, ymin=vert_min, ymax=vert_max, fill=left_right)) +
  geom_rect(colour="white", size=0.1) +
  geom_text(aes(x=median_x, y=median_y, size=size, label=pm_name, #all names of separate variables
                text=paste(party_name_english, " (",country_name,")", sep=""))) +
  scale_fill_manual(values=lacroix_palette("PassionFruit",type = "continuous", n=8)) + #matches left/right colours
  labs(title = "Timeline of European leaders since 2000",
       x = "year",
       y = "",
       fill = "Party's \nleft-right \nscore",
       size = NULL) +
  theme(axis.text.y = element_blank(), #y-axis doesn't have actual values; no need for labels
        axis.ticks.y = element_blank())
p <- ggplotly(p, tooltip = c("label", "text")) #how to select what shows on the tooltip

p
```

