---
name: geom_tile
permalink: ggplot2/geom_tile/
description: How to make a 2-dimensional heatmap in ggplot2 using geom_tile.
layout: base
thumbnail: thumbnail/geom_tile.jpg
language: ggplot2
page_type: example_index
display_as: basic
order: 8
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Basic geom\_tile graph
This graph, compiled by [Jeff Zimmerman](https://docs.google.com/spreadsheets/d/1HI-dikWN64clxSGJu2QV8C64R9Bkzt8K-jFaeHj4X7k/edit#gid=0), shows how often hitters swing and miss at fastballs, based on their velocity and spin rate. Colour schemes are from ColorBrewer; a complete list of palettes is available [here](https://ggplot2.tidyverse.org/reference/scale_brewer.html).

```{r}
library(plotly)
spinrates <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/spinrates.csv",
                      stringsAsFactors = FALSE)

p <- ggplot(spinrates, aes(x=velocity, y=spinrate)) +
  geom_tile(aes(fill = swing_miss)) +
  scale_fill_distiller(palette = "YlGnBu") +
  labs(title = "Likelihood of swinging and missing on a fastball",
       y = "spin rate (rpm)")

ggplotly(p)
```

### Adjusting appearance
The *direction* option sets which side of the colour scheme maps onto the low values and which side maps onto the high; it defaults to -1 but could be adjusted to 1.

Also [adjusted the theme](https://ggplot2.tidyverse.org/reference/ggtheme.html).

```{r}
library(plotly)
spinrates <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/spinrates.csv",
                      stringsAsFactors = FALSE)

p <- ggplot(spinrates, aes(x=velocity, y=spinrate)) +
  geom_tile(aes(fill = swing_miss)) +
  scale_fill_distiller(palette = "YlGnBu", direction = 1) +
  theme_light() +
  labs(title = "Likelihood of swinging and missing on a fastball",
       y = "spin rate (rpm)")

ggplotly(p)
```

### geom\_tile with viridis colour scheme
[Viridis colour schemes](https://ggplot2.tidyverse.org/reference/scale_brewer.html) are uniform in both colour and black-and-white, as well as for those with colour-blindness. There are five colour schemes: "magma" (or "A"), "inferno" (or "B"), "plasma" (or "C"), "viridis" (or "D", the default option) and "cividis" (or "E").

```{r}
library(plotly)
spinrates <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/spinrates.csv",
                      stringsAsFactors = FALSE)

p <- ggplot(spinrates, aes(x=velocity, y=spinrate)) +
  geom_tile(aes(fill = swing_miss)) +
  scale_fill_viridis_c(option = "B", direction = -1) +
  labs(title = "Likelihood of swinging and missing on a fastball",
       y = "spin rate (rpm)") +
  theme_light()

ggplotly(p)
```

