---
description: How to make interactive 3D surface plots in R.
display_as: 3d_charts
language: r
layout: base
name: 3D Surface Plots
order: 3
output:
  html_document:
    keep_md: true
page_type: example_index
permalink: r/3d-surface-plots/
thumbnail: thumbnail/3d-surface.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

# Basic 3D Surface Plot

```{r, results = "hide"}
library(plotly)
# volcano is a numeric matrix that ships with R
p <- plot_ly(z = ~volcano) %>% add_surface()

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="surface-1")
chart_link
```

```{r, echo=FALSE, height=800}
chart_link
```

# Surface Plot With Contours

```{r, results = "hide"}
library(plotly)
# volcano is a numeric matrix that ships with R
p <- plot_ly(z = ~volcano) %>% add_surface(
  contours = list(
    z = list(
      show=TRUE,
      usecolormap=TRUE,
      highlightcolor="#ff0000",
      project=list(z=TRUE)
      )
    )
  ) %>%
  layout(
    scene = list(
      camera=list(
        eye = list(x=1.87, y=0.88, z=-0.64)
        )
      )
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="surface-contours-1")
chart_link
```

```{r, echo=FALSE, height=800}
chart_link
```

### 2D Kernel Density Estimation

```{r, results = "hide"}
kd <- with(MASS::geyser, MASS::kde2d(duration, waiting, n = 50))
p <- plot_ly(x = kd$x, y = kd$y, z = kd$z) %>% add_surface()

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="surface-2")
chart_link
```

```{r, echo=FALSE, height=800}
chart_link
```

#### Configure Surface Contour Levels
This example shows how to slice the surface graph on the desired position for each of x, y and z axis. [contours.x.start](https://plot.ly/r/reference/#surface-contours-x-start) sets the starting contour level value, `end` sets the end of it, and `size` sets the step between each contour level.

```{r, results = "hide"}

x = c(1,2,3,4,5)
y = c(1,2,3,4,5)
z = rbind(
  c(0, 1, 0, 1, 0),
  c(1, 0, 1, 0, 1),
  c(0, 1, 0, 1, 0),
  c(1, 0, 1, 0, 1),
  c(0, 1, 0, 1, 0))


library(plotly)
p <- plot_ly(
  type = 'surface',
  contours = list(
    x = list(show = TRUE, start = 1.5, end = 2, size = 0.04, color = 'white'),
    z = list(show = TRUE, start = 0.5, end = 0.8, size = 0.05)),
  x = ~x,
  y = ~y,
  z = ~z) %>%
  layout(
    scene = list(
      xaxis = list(nticks = 20),
      zaxis = list(nticks = 4),
      camera = list(eye = list(x = 0, y = -1, z = 0.5)),
      aspectratio = list(x = .9, y = .8, z = 0.2)))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="surface-config")
chart_link
```

```{r, echo=FALSE, height=800}
chart_link
```

### Multiple Surfaces

```{r, results = "hide"}
z <- c(
  c(8.83,8.89,8.81,8.87,8.9,8.87),
  c(8.89,8.94,8.85,8.94,8.96,8.92),
  c(8.84,8.9,8.82,8.92,8.93,8.91),
  c(8.79,8.85,8.79,8.9,8.94,8.92),
  c(8.79,8.88,8.81,8.9,8.95,8.92),
  c(8.8,8.82,8.78,8.91,8.94,8.92),
  c(8.75,8.78,8.77,8.91,8.95,8.92),
  c(8.8,8.8,8.77,8.91,8.95,8.94),
  c(8.74,8.81,8.76,8.93,8.98,8.99),
  c(8.89,8.99,8.92,9.1,9.13,9.11),
  c(8.97,8.97,8.91,9.09,9.11,9.11),
  c(9.04,9.08,9.05,9.25,9.28,9.27),
  c(9,9.01,9,9.2,9.23,9.2),
  c(8.99,8.99,8.98,9.18,9.2,9.19),
  c(8.93,8.97,8.97,9.18,9.2,9.18)
)
dim(z) <- c(15,6)
z2 <- z + 1
z3 <- z - 1

p <- plot_ly(showscale = FALSE) %>%
  add_surface(z = ~z) %>%
  add_surface(z = ~z2, opacity = 0.98) %>%
  add_surface(z = ~z3, opacity = 0.98)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="surface-3")
chart_link
```

```{r, echo=FALSE, results='markup', height=800}
chart_link
```