---
name: 3D Tri-Surf Plots
permalink: r/trisurf/
description: How to make interactive 3D mesh plots in R.
layout: base
thumbnail: thumbnail/trisurf.jpg
language: r
display_as: 3d_charts
order: 17
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```
### Basic Tri-Surf Plot

```{r}
library(plotly)

p <- plot_ly(
  x = c(0, 1, 2, 0),
  y = c(0, 0, 1, 2),
  z = c(0, 2, 0, 1),
  i = c(0, 0, 0, 1),
  j = c(1, 2, 3, 2),
  k = c(2, 3, 1, 3),
  facecolor = toRGB(viridisLite::viridis(4))
)

p
```


### Cube with Different Face Colors

```{r}
library(plotly)

p <- plot_ly(
  x = c(0, 0, 1, 1, 0, 0, 1, 1),
  y = c(0, 1, 1, 0, 0, 1, 1, 0),
  z = c(0, 0, 0, 0, 1, 1, 1, 1),
  i = c(7, 0, 0, 0, 4, 4, 2, 6, 4, 0, 3, 7),
  j = c(3, 4, 1, 2, 5, 6, 5, 5, 0, 1, 2, 2),
  k = c(0, 7, 2, 3, 6, 7, 1, 2, 5, 5, 7, 6),
  facecolor = rep(toRGB(viridisLite::inferno(6)), each = 2)
)

p
```

### Helicopter

```{r}
library(plotly)
library(geomorph)

plyFile <- 'http://people.sc.fsu.edu/~jburkardt/data/ply/chopper.ply'
dest <- basename(plyFile)
if (!file.exists(dest)) {
  download.file(plyFile, dest)
}

mesh <- read.ply(dest)
# see getS3method("shade3d", "mesh3d") for details on how to plot

# plot point cloud
x <- mesh$vb["xpts",]
y <- mesh$vb["ypts",]
z <- mesh$vb["zpts",]
m <- matrix(c(x,y,z), ncol=3, dimnames=list(NULL,c("x","y","z")))

# now figure out the colormap
zmean <- apply(t(mesh$it),MARGIN=1,function(row){mean(m[row,3])})

library(scales)
facecolor = colour_ramp(
  brewer_pal(palette="RdBu")(9)
)(rescale(x=zmean))

p <- plot_ly(
  x = x, y = y, z = z,
  i = mesh$it[1,]-1, j = mesh$it[2,]-1, k = mesh$it[3,]-1,
  facecolor = facecolor,
  type = "mesh3d"
)

p
```

### Maps

```{r}
#devtools::install_github("hypertidy/anglr")
library(anglr)
library(maptools)
library(plotly)
data(wrld_simpl)

map1 <- subset(wrld_simpl,
               NAME %in% c("Indonesia", "Papua New Guinea", "New Zealand", "Australia"))
## DEL model (like TRI in silicate)
delmesh <-  anglr::globe(anglr::DEL(map1, max_area = 0.5))
mesh <- as.mesh3d(delmesh)


# plot point cloud
x <- mesh$vb[1,]
y <- mesh$vb[2, ]
z <- mesh$vb[3,]
m <- matrix(c(x,y,z), ncol=3, dimnames=list(NULL,c("x","y","z")))

# colours in z don't make sense here, need to map object aesthetics above
zmean <- apply(t(mesh$it),MARGIN=1,function(row){mean(m[row,3])})

library(scales)
facecolor = colour_ramp(
  brewer_pal(palette="RdBu")(9)
)(rescale(x=zmean))

p <- plot_ly(
  x = x, y = y, z = z,
  i = mesh$it[1,]-1, j = mesh$it[2,]-1, k = mesh$it[3,]-1,
  facecolor = facecolor,
  type = "mesh3d"
)

p
```
Inspired by <a href="http://rpubs.com/cyclemumner/rangl-plotly"> Michael Sumner</a>
