---
title: 3D Cone Plots in R | Examples | Plotly
name: 3D Cone Plots
permalink: r/cone-plot/
description: How to make 3D cone plots with Plotly.
layout: base
thumbnail: thumbnail/3dcone.png
language: r
has_thumbnail: true
display_as: 3d_charts
order: 18
redirect_from: r/3d-cone/
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r}
library(plotly)
packageVersion('plotly')
```

### Basic 3D Cone

``` {r, results = 'hide'}
library(plotly)

p <- plot_ly(
  type= "cone",
  x= 1, y= 1, z= 1,
  u= 1, v= 1, w= 0
  ) %>%
  layout(
    scene= list(
      camera= list(
        eye= list(x= -0.76, y= 1.8, z= 0.92)
      )
    )
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="cone-basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Mulitple 3D Cones

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
  type="cone",
  x= c(1, 2, 3),
  y= c(1, 2, 3),
  z= c(1, 2, 3),
  u= c(1, 0, 0),
  v= c(0, 3, 0),
  w= c(0, 0, 2),
  sizemode= "absolute",
  sizeref= 2,
  anchor= "tip",
  colorbar= list(
    x= 0,
    xanchor= "right",
    side= "left"
  )
) %>%
  layout(
    scene= list(
      domain= list(x= c(0, 1)),
      camera= list(
        eye= list(x= -1.57, y= 1.36, z= 0.58)
      )
    )
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="cone-multiple")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### 3D Cone Lighting

```{r, results = 'hide'}
library(plotly)

p <- plot_ly(
    type="cone",
    y= c(1, 2, 3),
    z= c(1, 1, 1),
    u= c(1, 2, 3),
    v= c(1, 1, 2),
    w= c(4, 4, 1),
    showscale= F,
    hoverinfo= "u+v+w+name"
  ) %>%
  add_trace(
    name= "base",
    x= c(1, 1, 1)
  ) %>%
  add_trace(
    name= "opacity=0.3",
    x= c(2, 2, 2),
    opacity= 0.3
  ) %>%
  add_trace(
    name= "lighting.ambient=0.3",
    x= c(3, 3, 3),
    lighting= list(ambient= 0.3)
  ) %>%
  add_trace(
    name= "lighting.diffuse=0.3",
    x= c(4, 4, 4),
    lighting= list(diffuse= 0.3)
  ) %>%
  add_trace(
    name= "lighting.specular=2",
    x= c(5, 5, 5),
    lighting= list(specular= 2)
  ) %>%
  add_trace(
    name= "lighting.roughness=1",
    x= c(6, 6, 6),
    lighting= list(roughness= 1)
  ) %>%
  add_trace(
    name= "lighting.fresnel=2",
    x= c(7, 7, 7),
    lighting= list(fresnel= 2)
  ) %>%
  add_trace(
    name= "lighting.position x=0,y=0,z=1e5",
    x= c(8, 8, 8),
    lightposition= list(x= 0, y= 0, z= 1e5)
  ) %>%
    layout(
      scene= list(
        aspectmode= "data",
        camera= list(
          eye= list(x= 0.05, y= -2.6, z= 2)
        )
      ),
      margin= list(t= 0, b= 0, l= 0, r= 0)
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="cone-lighting")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### 3D Cone of Wind Dataset

```{r, results = 'hide'}
library(plotly)
library(rjson)

dat <- fromJSON(file='https://raw.githubusercontent.com/plotly/plotly.js/master/test/image/mocks/gl3d_cone-wind.json')

p <- plot_ly(
  type="cone",
  x= dat$data[[1]]$x,
  y= dat$data[[1]]$y,
  z= dat$data[[1]]$z,
  u= dat$data[[1]]$u,
  v= dat$data[[1]]$v,
  w= dat$data[[1]]$w,
  text="-> wind <-",
  hoverinfo="u+v+w+text",
  marker = list(
    colorscale = "Viridis",
    cmin=0,
    cmax=100
  )
) %>%
layout(
  scene= list(
    aspectratio= list(x= -1.57, y= 1.36, z= 0.58)
  )
)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="cone-wind")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### 3D Cone Vortex

```{r, results = 'hide'}
library(plotly)
library(rjson)

df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/vortex.csv')

p <- plot_ly(
  df,
  type="cone",
  x= ~x,
  y= ~y,
  z= ~z,
  u= ~u,
  v= ~v,
  w= ~w,
  sizemode= 'absolute',
  sizeref= 40
) %>%
layout(
  scene= list(
    aspectratio= list(x= 1, y= 1, z= 0.8),
    camera = list(eye = list(x= 1.2, y= 1.2, z= 0.6))
  )
)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="cone-vortex")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Reference

See [https://plot.ly/r/reference/](https://plot.ly/r/reference/) for more information and chart attribute options!
