---
name: 3D Isosurface Plots 
permalink: r/3d-isosurface-plots/
description: How to create 3D isosurface plots with Plotly.
layout: base
thumbnail: thumbnail/isosurface.jpg
language: r
display_as: 3d_charts
order: 20
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```


#### Basic Isosurface Plot

```{r}
library(plotly)

p <- plot_ly(
  type='isosurface',
  x = c(0,0,0,0,1,1,1,1),
  y = c(1,0,1,0,1,0,1,0),
  z = c(1,1,0,0,1,1,0,0),
  value = c(1,2,3,4,5,6,7,8),
  isomin=2,
  isomax=6
  )

p
```

#### Isosurface with Additional Slices

```{r}
library(plotly)

df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/clebsch-cubic.csv')

p <- plot_ly(
  df,
  type='isosurface',
  x = ~x,
  y = ~y,
  z = ~z,
  value = ~value,
  isomin = -100,
  isomax = 100,
  colorscale='RdBu',
  surface = list(show = TRUE, count = 1),
  slices = list(z = list(
          show = TRUE, locations = c(-0.3, 0.5)
  )),
  caps = list(
    x = list(show = FALSE),
    y = list(show = FALSE),
    z = list(show = FALSE)
    )
) %>%
  layout(
    margin=list(t = 0, l = 0, b = 0),
    scene=list(
        camera=list(
            eye=list(
                x = 1.86,
                y = 0.61,
                z = 0.98
            )
        )
    )
)

p
```

#### Multiple Isosurfaces with Caps

```{r}
library(plotly)

df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/clebsch-cubic.csv')

p <- plot_ly(
  df,
  type='isosurface',
  x = ~x,
  y = ~y,
  z = ~z,
  value = ~value,
  isomin = -10,
  isomax = 10,
  surface = list(show = TRUE, count = 4, fill = 0.8, pattern = 'odd'),
  caps = list(
    x = list(show = TRUE),
    y = list(show = TRUE),
    z = list(show = TRUE)
    )
) %>%
  layout(
    margin=list(t = 0, l = 0, b = 0),
    scene=list(
        camera=list(
            eye=list(
                x = 1.86,
                y = 0.61,
                z = 0.98
            )
        )
    )
)

p
```


#### Reference

See our [reference page](https://plot.ly/r/reference/) for more information and chart attribute options!.
