---
title: Multiple Axes in R | Plotly
name: Multiple Axes
permalink: r/multiple-axes/
description: How to make a graph with multiple axes in R with Plotly.
layout: base
thumbnail: thumbnail/multiple-axes.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: multiple_axes
order: 1
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Multiple Y Axes

```{r, results = 'hide'}
library(plotly)
ay <- list(
  tickfont = list(color = "red"),
  overlaying = "y",
  side = "right",
  title = "second y axis"
)
p <- plot_ly() %>%
  add_lines(x = ~1:3, y = ~10*(1:3), name = "slope of 10") %>%
  add_lines(x = ~2:4, y = ~1:3, name = "slope of 1", yaxis = "y2") %>%
  layout(
    title = "Double Y Axis", yaxis2 = ay,
    xaxis = list(title="x")
  )

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="axes-mulitple")
chart_link
```


```{r, echo=FALSE}
chart_link
```
