---
title: Subplots in R | Plotly
name: Subplots
permalink: r/subplots/
description: How to graph subplots and small multiples in R with Plotly.
layout: base
thumbnail: thumbnail/subplots.jpg
language: r
page_type: example_index
has_thumbnail: true
display_as: multiple_axes
order: 2
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```
### Basic Subplots

The subplot() function provides a flexible interface for merging plotly objects into a single object (i.e., view).

```{r, results = 'hide'}
library(plotly)
p1 <- plot_ly(economics, x = ~date, y = ~unemploy) %>%
  add_lines(name = ~"unemploy")
p2 <- plot_ly(economics, x = ~date, y = ~uempmed) %>%
  add_lines(name = ~"uempmed")
p <- subplot(p1, p2)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link <- api_create(p, filename = "subplot-basic")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Scaled Subplots

Although subplot() accepts an arbitrary number of plot objects, passing a list of plots can save typing and redundant code when dealing with a large number of plots. For example, you can share the x-axis by utlising shareX, set axis ID, and and specify the number of of rows with nrows.

```{r, results = 'hide'}

p <- economics %>%
  tidyr::gather(variable, value, -date) %>%
  transform(id = as.integer(factor(variable))) %>%
  plot_ly(x = ~date, y = ~value, color = ~variable, colors = "Dark2",
          yaxis = ~paste0("y", id)) %>%
  add_lines() %>%
  subplot(nrows = 5, shareX = TRUE)

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link <- api_create(p, filename = "subplot-scale-y")
chart_link
```

```{r, echo=FALSE}
chart_link
```

### Recursive Subplots

The subplot() function returns a plotly object so it can be modified like any other plotly object. This effectively means that subplots work recursively (i.e., you can have subplots within subplots).

```{r, results = 'hide'}
plotList <- function(nplots) {
  lapply(seq_len(nplots), function(x) plot_ly())
}
s1 <- subplot(plotList(6), nrows = 2, shareX = TRUE, shareY = TRUE)
s2 <- subplot(plotList(2), shareY = TRUE)
p <- subplot(s1, s2, plot_ly(), nrows = 3, margin = 0.04, heights = c(0.6, 0.3, 0.1))

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link <- api_create(p, filename = "subplot-recursive")
chart_link
```

```{r, echo=FALSE}
chart_link
```

For more information on subplots check [the plotly book](https://cpsievert.github.io/plotly_book/merging-plotly-objects.html)
