---
name: Inset Plots
permalink: r/insets/
description: How to make an inset plot in R with Plotly
layout: base
thumbnail: thumbnail/insets.jpg
language: r
page_type: example_index
display_as: multiple_axes
order: 3
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Basic Inset

See also the [chapter on subplots in the plotly book](https://cpsievert.github.io/plotly_book/subplot.html)

```{r}
library(plotly)
p <- plotly::plot_ly()
p <- plotly::add_trace(p, x = c(1, 2, 3), y = c(4, 3, 2), mode='lines')
p <- plotly::add_trace(p, x = c(20, 30, 40), y = c(30, 40, 50), xaxis='x2', yaxis='y2', mode='lines')
p <- plotly::layout(p, xaxis2 = list(domain = c(0.6, 0.95), anchor='y2'),
         yaxis2 = list(domain = c(0.6, 0.95), anchor='x2'))
         
p
```
