---
title: WebGL in Plotly and R| Examples | Plotly
name: WebGL in Plotly and R
permalink: r/webgl-vs-svg-million-points/
description: How to create plots using WebGL and Plotly
layout: base
language: r
page_type: example_index
output: 
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```

### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.

```{r, results = 'hide'}
library(plotly)
packageVersion('plotly')
```

# WebGL with 1 Million points 

```{r, results = 'hide'}
library(plotly)

n <- 1e6
x <- rnorm(n)
y <- 2*x + rnorm(n, sd = 5)

p <- plot_ly(x = x, y = y, alpha  = 0.01) %>% toWebGL()

# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="webgl-1e6")
chart_link
```

```{r, echo=FALSE}
chart_link
```

# Reference

See [scattergl](https://plot.ly/r/reference/#scattergl) for more information. 
