---
description: How to download Chart Studio users' public graphs and data into an R session.
display_as: chart_studio
language: r
layout: base
name: Working With Chart Studio Graphs
order: 6
output:
  html_document:
    keep_md: true
permalink: r/working-with-chart-studio-graphs/
redirect_from:
- r/get-requests/
thumbnail: thumbnail/hover.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### Download Chart Studio Graphs Into R Sessions

Download Chart Studio figures directly into your R session with the `api_download_plot()` function. This takes the `plot_id` of the Chart Studio plot and the `username` of the plot's creator as arguments.

For example, to download [https://plot.ly/~cpsievert/559](https://plot.ly/~cpsievert/559) into R, call:

```{r}
library(plotly)
fig <- api_download_plot("559", "cpsievert")
fig
```

### Update The Layout on A Downloaded Graph

Once the figure is downloaded from Chart Studio into your R session, you can update its layout just like you would any other figure you create with the `plotly` R package. 

**Note:** If you were to re-upload this figure to Chart Studio, a new figure would be created unless you specify the same `filename` as the figure that you downloaded. In that case, the existing figure will be overwritten.

```{r}
p <- layout(fig, title = paste("Modified on ", Sys.time()))
p
```

### Adding a Trace to a Subplot Figure

```{r}
fig <- api_download_plot("6343", "chelsea_lyn")

p <- add_lines(fig, x = c(1, 2), y = c(1, 2), xaxis = "x2", yaxis = "y2")
p
```

### Reference

See the documentation for [getting started with Chart Studio in R](https://plot.ly/r/getting-started-with-chart-studio). 