---
description: How to embed R graphs in RMarkdown files.
display_as: chart_studio
language: r
layout: base
name: Embedding Graphs in RMarkdown Files
order: 3
output:
  html_document:
    keep_md: true
page_type: example_index
permalink: r/embedding-graphs-in-rmarkdown/
redirect_from:
- r/embedding-plotly-graphs-in-HTML
- r/knitr/
thumbnail: thumbnail/ipythonnb.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### Embedding R Graphs in RMarkdown files

If you are creating R charts in an [RMarkdown](http://rmarkdown.rstudio.com/) environment with HTML output (such as RStudio), simply printing a graph you created using the `plotly` R package in a code chunk will result in an interactive HTML graph in the viewer. 

When using RMarkdown with non-HTML output, printing a graph you created using the `plotly` R package will result in a `.png` screenshot of the graph being generated.

```{r}
library(plotly)
p <- plot_ly(economics, x = ~date, y = ~unemploy / pop)
p
```

Sometimes, you may want to print a _list_ of graphs in an RMarkdown document. 

If, for some reason, you don't want to use the [`subplot()` function](https://plot.ly/r/subplots/), you can render a list of `htmlwidgets` in a single code chunk using the `tagList()` function from the [`htmltools`](https://cran.r-project.org/web/packages/htmltools/index.html) package:

```{r}
htmltools::tagList(list(p, p))
```

Another way to print multiple graphs in an RMarkdown document with the `plotly` R package is by using the [`lapply`](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/lapply) function:

```{r}
library(plotly)

htmltools::tagList(lapply(1:3, function(x) { plot_ly(x = rnorm(10)) }))
```

Alternatively, you can use a `for` loop instead of `lapply`:

```{r}
library(plotly)

l <- htmltools::tagList()
for (i in 1:3) {
  l[[i]] <- plot_ly(x = rnorm(10))
}
l
```

### Embedding Chart Studio Graphs in RMarkdown Files

When you publish your plots to Chart Studio via the `api_create()` function, a figure object is returned to your R session. 

When a Chart Studio figure object is rendered in an RMarkdown document, it is embedded as an `iframe`, displaying the plot as it appears on your Chart Studio account.

```{r, echo="FALSE", results='hide'}
f <- api_create(p)
class(f)
f
```

You can control the height and width of that `iframe` through the `height`/`width` [knitr chunk options](http://yihui.name/knitr/options/), but the figure object also contains the relevant URL so you have complete control over embedding your figure. 

This [post](http://help.plot.ly/embed-graphs-in-websites/) has more details on how to embed Chart Studio graphs within HTML `iframes`, but you could also use Chart Studio's built-in image export by simply adding a `.png` or `.jpeg` file extension to the end of the figure's URL. 

For example, view the static image of <https://plot.ly/~chris/1638> at <https://plot.ly/~chris/1638.png>.