---
description: How to embed Plotly graphs in Rmd files.
display_as: chart_studio
language: r
layout: base
name: Embedding Graphs with Knitr
order: 3
output:
  html_document:
    highlight: null
    keep_md: true
    theme: null
page_type: example_index
permalink: r/knitr/
redirect_from:
- r/embedding-plotly-graphs-in-HTML
thumbnail: thumbnail/ipythonnb.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

### Embedding plotly graphs in Rmd files

If you are using [rmarkdown](http://rmarkdown.rstudio.com/) with HTML output, printing a `plotly` object in a code chunk will result in an interactive HTML graph. When using rmarkdown with non-HTML output, printing a `plotly` object will result in a png screenshot of the graph.

```{r, results = "hide"}
library(plotly)
p <- plot_ly(economics, x = ~date, y = ~unemploy / pop)
```

```{r, echo=FALSE}
api_create(p, filename='r-docs/knitr-example')
```

Sometimes, you may want to print a _list_ of plotly objects. If, for some reason, you don't want to use the [`subplot()` function](https://plot.ly/r/subplots/), you can print a list of htmlwidgets in a single code chunk using the `tagList()` function from the **htmltools** package:

```{r, results = "hide"}
htmltools::tagList(list(p, p))
```

Another way to print multiple objects is by using a `lapply`:

```{r, results = "hide"}
library(plotly)

htmltools::tagList(lapply(1:3, function(x) { plot_ly(x = rnorm(10)) }))
```

Alternatively, you can use for loops:

```{r, results = "hide"}
library(plotly)

l <- htmltools::tagList()
for (i in 1:3) {
  l[[i]] <- plot_ly(x = rnorm(10))
}
l
```

You can also host your figures on a plotly server via `api_create()` which returns a figure object. When a figure object is printed in an rmarkdown/knitr document, it embeds the figure as an iframe, displaying the plot as it appears on your plotly account.

```{r, results='hide'}
f <- api_create(p)
class(f)
f
```

You can control the height/width of that iframe through the `height`/`width` [knitr chunk options](http://yihui.name/knitr/options/), but the figure object also contains the relevant url so you complete control over embedding your figure. The post has more details on how to [embed plotly graphs with HTML iframes](http://help.plot.ly/embed-graphs-in-websites/), but could also use plotly's built-in image export by simply adding a `.png` (or similar) extension.

```{r}
htmltools::tags$img(src = paste0(f[["url"]], ".png"))
```
