---
description: How to set the privacy settings of plotly graphs in R.
display_as: chart_studio
language: r
layout: base
name: Public vs Private Graphs
order: 7
output:
  html_document:
    keep_md: true
permalink: r/privacy/
thumbnail: thumbnail/privacy.jpg
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
Sys.setenv("plotly_username"="RPlotBot")
Sys.setenv("plotly_api_key"="q0lz6r5efr")
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check
Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Default Privacy
Plotly for R renders entirely locally by default, but you can also publish these graphs to the web via the `api_create()` function. By default, `api_create()` creates public graphs (which are free to create), but with a [plotly subscription](https://plot.ly/products/cloud/) you can easily make them private via the `sharing` argument.

### Public Graph
Please note, this is the default privacy option.

```{r, results = 'hide'}
library(plotly)
p <- plot_ly(x = c(0, 2, 4), y = c(0, 4, 2), type = 'scatter', mode = 'markers+lines')
chart_link = api_create(p, filename = "public-graph")
chart_link
```

```{r, echo=FALSE}
chart_link
```

Below is the URL of this public plot. Anyone can view public plots even if they are not logged into Plotly. <br> Try it out: [https://plot.ly/~RPlotBot/4545](https://plot.ly/~RPlotBot/4545)

### Private Graph
```{r, results = 'hide'}
library(plotly)
p <- plot_ly(x = c(0, 2, 4), y = c(0, 4, 2), type = 'scatter', mode = 'markers+lines')
chart_link = api_create(p, filename = "private-graph", sharing = "private")
chart_link
```

```{r, echo=FALSE}
chart_link
```

Below is the URL of the private plot above. Only the owner can view the private plot. You won't be able to view this plot. <br> Try it out: [https://plot.ly/~RPlotBot/4549/](https://plot.ly/~RPlotBot/4549/)

### Secret Graph
```{r, results = 'hide'}
library(plotly)
p <- plot_ly(x = c(0, 2, 4), y = c(0, 4, 2), type = 'scatter', mode = 'markers+lines')
chart_link = api_create(p, filename = "secret-graph", sharing = "secret")
chart_link
```

```{r, echo=FALSE}
chart_link
```

Below is the URL of this secret plot. Anyone with the secret link can view this chart. However, it will not appear in the Plotly feed, your profile, or search engines. <br> Try it out:
[https://plot.ly/~RPlotBot/4553/?share_key=62AMQ8YBpZebu6Y5OYsukj](https://plot.ly/~RPlotBot/4553/?share_key=62AMQ8YBpZebu6Y5OYsukj)
