---
name: Configuration Options For Embedded Chart Studio Graphs 
permalink: r/configuration-options/
description: How to set configuration options of embedded Chart Studio graphs in R. Examples of both online and offline configurations.
layout: base
language: r
thumbnail: thumbnail/modebar-icons.png
display_as: chart_studio
order: 7
output:
  html_document:
    keep_md: true
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning=FALSE)
```
### New to Plotly?

Plotly's R library is free and open source!<br>
[Get started](https://plot.ly/r/getting-started/) by downloading the client and [reading the primer](https://plot.ly/r/getting-started/).<br>
You can set up Plotly to work in [online](https://plot.ly/r/getting-started/#hosting-graphs-in-your-online-plotly-account) or [offline](https://plot.ly/r/offline/) mode.<br>
We also have a quick-reference [cheatsheet](https://images.plot.ly/plotly-documentation/images/r_cheat_sheet.pdf) (new!) to help you get started!

### Version Check

Version 4 of Plotly's R package is now [available](https://plot.ly/r/getting-started/#installation)!<br>
Check out [this post](http://moderndata.plot.ly/upgrading-to-plotly-4-0-and-above/) for more information on breaking changes and new features available in this version.
```{r}
library(plotly)
packageVersion('plotly')
```

#### Online Configuration Options 

Configuration options for graphs created with the `plotly` R package are overridden when those graphs are published to Chart Studio using the `api_create()` function. 

To set configutation options for charts published to Chart STudio, you can edit the plot's embed url. 

Visit our [embed tutorial](http://help.plot.ly/embed-graphs-in-websites/#step-8-customize-the-iframe) for more information on customizing the embed URL to remove the "Edit Chart" link, hide the modebar, or autosize the plot.

#### Offline Configuration Options 

Add the 'Edit Chart' link:
```{r, results = 'hide'}
library(plotly)
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length)

htmlwidgets::saveWidget(config(p, showLink = T), "graph.html")
```

Remove the 'mode bar':
```{r, results = 'hide'}
htmlwidgets::saveWidget(config(p, displayModeBar = FALSE), "graph.html")
```

#### Reference
Arguments are documented [here](https://github.com/plotly/plotly.js/blob/master/src/plot_api/plot_config.js).
```r
?config
```